### 2018-10-24 paper.tex
10-24

\documentclass[runningheads]{llncs}
\usepackage{graphicx}

\begin{document}
\title{Explain urban regional function}
\author{Submission}

\maketitle

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Explanation  \and Urban computing \and Sentiment analysis.}
\end{abstract}
%

\section{Introduction}

\subsection{motivation}
Urban computing is defined by Zheng et al. ~\cite{Zheng2014UrbanConcepts} as an concept where many factors ,such as sensors,prople,vehicles and so on, consist of a dynamic urban system.The aims of urban computing include improve the life level of residents,optimizing urban planning, decreasing traffic jams, reducing various pollution and so on.
With the improvement of living life of urban residents,GPS-embedded taxi begin to play an important part of urban computing.And the data of taxi mobility provide us an valuable way to compute urban system.For example,Zheng et al. ~\cite{Zheng2011taxicabs} detect the flaws in the existing urban planning of a city using the GPS trajectories of taxis traveling in the urban areas. Meng et al.\cite{Meng2017Traffic} propose a framework to infer the city-wide traffic volume information with loop detectors and taxi trajectories.Garg et al.\cite{Garg2018Route}minimizing distance through Monte Carlo tree search to decrease the rate of empty carrying and improve taxi drivers’ profits.
As you can see, Urban computing is closely linked with urban life.

Discovering regions of different function is a step towards urban computing.In this direction,Yuan et al.~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion,Yuan2018FunctionRegion} do well in discovering regions of different functions %3 references.
%~\cite{Yuan2012FunctionRegion}~\cite{Yuan2015FunctionRegion}:latent activity trajectories~\cite{Yuan2018FunctionRegion}

\subsection{explain power}
%Previous model
The approaches to explanation recommendation system was developing recently.At the early time,the fundamental methods of personal recommendation is recommendation systems with user-based and item-based. Resnick et al.\cite{Resnick1994UserBased} found user-based collaboration filtering recommendation system.The explanation is the similar neighbors whose interests and rates tend to be consistent with target user.Analogously,Sarwar et al. \cite{Sarwar2001ItemBased} proposed the recommendation with item-based could find the suitable items which has similar features with purchased items.

%model complex, deep model
Variants of these basic model constitute the majority of explanation recommendation systems.e.g.,Pazzani et al.\cite{Pazzani2007ContentBased}
As time going

%data heterogenous 
%explainability -> disadvantage

%Explaining the result is of crucial importance
We can see that early recommendation systems tend to base on intuition and full with common sense,which improve users' satisfaction easily. Now the explanation recommendation systems is developing with more accuracy , which generate more satisfying results.Nevertheless ,the complexity of models is increasing at the meantime,which covers the intuition of whole structure and weakens the persuasiveness of models.So the explanation is playing an important part in recommendation systems.%~\cite{{Zhang2018SIGIR}}
Majority of users trust and choice satisfaction were highly correlated with the reliability of the explanations for recommendations.Herlocker et al.~\cite{Herlocker2000Explanation}  do an investigation which shows that explanation facilities can improve the acceptance of recommendation systems.The following experiments,e.g.,by Ferwerda et al.~\cite{Ferwerda2012ContentCorrelate} has proven the conclusion.We aim to propose models to explain the destination why we recommend it more persuasively

%explain implementation, we need to incorporate activity and online sentiment
Our goal is to proposed a model to predict taxi destination and provide persuasive explanation for it.
%Furthermore, provide xxx explaination, activity , focus on aspects

\begin{figure}
    \centering
    \includegraphics[scale=0.25]{Structure.png}
    \caption{The general structure of our paper}
    %\label{fig:my_label}
\end{figure}

\subsection{problem}
For solve the problem,we face two challenges.One of it is...and the other is ...
segment regions = group regions with similar functions

function = distribution of activitys and opinions

%challenge

previous research

%opinion

%second challenge: time bins

\subsection{contribution}
Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item According to what I have learned,we are the first one to state-of-the-art
  \item 2
  \item 3
\end{itemize}

\subsection{paper structure}
The remainder of the paper is organized as follows. 
We give an overview for related work in Section 2.
In Section 3, we introduce our novel models as well as proving their logic.
Section 4 presents the suprior result in experiments of our models.
Finally, we made a conclusion and looked forward to our future work in Section 5.

\section{Related Work}

Two lines of work are related to this paper: sentiment analysis into human mobility,content from social media also provide great help for us. Many scholars have made fundamental contributions,and we combined them to find interesting patterns and extended the application .

To the best of our knowledges,we are the first to combined the sentiment into human mobility.

%related work section name, find another suitable name for mobility mining
\subsection{Urban Computing}

Urban computing~\cite{Zheng2014UrbanConcepts} tackles the major issues that cities face by analyzing human mobility collected from different sensors.  
Major sources of human mobility data are checkins in POI~\cite{}, pick-up and drop-off behavior of taxicabs~\cite{} in different locations and  trajectories~\cite{}.
%extract the different among these data
For checkins data, the most commonly adopted model is.
For taxicabs data, to fully utilize pick-up and drop-off, xxx is adopted to enhance xxx
For trajectory data, as it involves multiple points

%tasks
The aim of mobility mining is to uncover informative patterns of improve incomes of taxi drivers~\cite{}, attracts an increasing research interest~\cite{}. 
However, existing urban computing systems extensively rely on complex machine learning algorithms hence they act as blank-boxes for end users. 
The lack of explainability weakens the persuasiveness and trustworthiness of the system for users
Our work is to provide intuitive explanations of the results for users or system designers
%most of them adopt a topic model, treating mobility patterns as words~\cite{}%topic models

\subsection{Geographical Analysis of Online Sentiment}

Recently, an emrging research interest is witnessed in exploring the geographical factors that affect online sentiment.
Empirical studies have been conducted on large-scale human mobility data, such as checkins~\cite{}, trajectory, xxx~\cite{}
Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{milan15},a high check-in density region usually presents a more positive moode~\cite{},

%complete survey
However, most existing work of this line employ simple statistical analysis to uncover the associations. 
Such a coarse-grained analysis is distorted by latent variables, such as activity of the region.
Our work is the first to incorporate activity to obtain a fine-grained analysis.

\iffalse
\section{Application}
Our models have a wide range of application and their value
\subsection{Billboard}
Billboard
\subsection{Trajectory}
\fi

\section{Experiments}

\subsection{Data Set}
The data set for our experiments including both mobility data and content data.
The mobility data including the pick-up and drop-off time and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.

\subsection{Preparation}

\subsection{Baseline and other comparison}

\subsection{Evaluation Metrics}

\subsection{result}

\section{Conclusion}
In this paper , we proposed several models to find the most possible destination region for users and add explanation for it to enhance its persuasiveness.
The models have improve some extra recognition accuracy ,which have an extra contribution for functional city.

\begin{thebibliography}{25}
\bibitem{Zheng2014UrbanConcepts}Zheng Y, Capra L, Wolfson O, et al. Urban Computing:Concepts, Methodologies, and Applications[J]. Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.
    %综述城市计算的概念和框架
\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
    %利用GPS轨迹检测出现有城市规划中存在的缺陷。结果包括：1）存在显著交通问题的区域对，2）连接结构以及它们之间的相关性。这些结果可以评估所实施的规划的有效性，例如一个城市新建的公路和地铁线路，并提醒城市规划者在构思未来规划时没有认识到的问题。
\bibitem{Meng2017Traffic} Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y. City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories. Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10 
    %提出了一个框架来推断城市交通流量信息与环路探测器和出租车轨迹。
\bibitem{Garg2018Route}Garg, N.; Ranu, S. Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer! Proceedings of the 24th ACM SIGKDD International Conference on Knowledge Discovery \& 38; Data Mining,ACM,2018, 1425-1434 
    %通过Minimizing Distance through Monte Carlo Tree Search来对出租车司机进行路线推荐，使其提高效率，降低空载率。
\bibitem{Yuan2012FunctionRegion}Yuan J, Zheng Y, Xie X. Discovering regions of different functions in a city using human mobility and POIs[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. ACM, 2012:186-194.
    %套用LDA，根据功能划分城市区域
\bibitem{Yuan2015FunctionRegion}Yuan N J, Zheng Y, Xie X, et al. Discovering Urban Functional Zones Using Latent Activity Trajectories[J]. Knowledge \& Data Engineering IEEE Transactions on, 2015, 27(3):712-725.
    %
\bibitem{Yuan2018FunctionRegion}Yuan N J, Zheng Y, Xie X. Discovering Functional Zones in a City Using Human Movements and Points of Interest[J]. 2018.
    %
\bibitem{Resnick1994UserBased}Resnick P, Iacovou N, Suchak M, et al. GroupLens:an open architecture for collaborative filtering of netnews[C]// ACM Conference on Computer Supported Cooperative Work. ACM, 1994:175-186.
    %提出user-based collaboration filtering
\bibitem{Sarwar2001ItemBased}Sarwar B, Karypis G, Konstan J, et al. Item-based collaborative filtering recommendation algorithms[C]// International Conference on World Wide Web. ACM, 2001:285-295.
    %提出item-based collaboration filtering
\bibitem{Pazzani2007ContentBased}Pazzani M J, Billsus D. Content-based recommendation systems[M]// The adaptive web. Springer-Verlag, 2007:325-341.
    %提出content-based collaboration filtering    
\bibitem{Alshamsi15milan}Alshamsi A, Awad E, Almehrezi M, et al. Misery loves company: happiness and communication in the city[J]. Epj Data Science, 2015, 4(1):7.
    %把米兰城区划分成100*100区域，根据社交网络发现情绪积极的region更喜欢和其他积极的region交流。
\bibitem{Gallegos16happier}Gallegos L, Huang A, Huang A, et al. Geography of Emotion: Where in a City are People Happier?[C]// International Conference Companion on World Wide Web. International World Wide Web Conferences Steering Committee, 2016:569-574.
    %将其他人的统计方法用于划分区域的签到数据集中，比较得出结论：①签到数据越多的地方积极性越高，消极性越低。②发现在签到数据多的地方签到的用户，活动范围都比较大。可以理解为这个地方比较吸引人，人们愿意走更远的路去这里玩。③结合人口普查的结果，发现签到数据多的地方所居住的居民年龄更大、非西班牙裔人口更多、受教育程度更高
\bibitem{Zhao2016POI}Zhao S, King I, Lyu M R. A Survey of Point-of-interest Recommendation in Location-based Social Networks[J]. 2016.
    %对截止16年最新的50篇与LSBN和POI相关的顶会论文做了一个总结，不知道能不能用上
\bibitem{Zhang2018SIGIR} Zhang, Y.; Zhang, Y.; Zhang, M. SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018) //The 41st International ACM SIGIR Conference on Research \& 38; Development in Information Retrieval,ACM,2018, 1411-1413 
    %概述了推荐系统中explanation的重要性
\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. 2018.
    %介绍了推荐系统解释的调查概述和未来新视角。主要看了explanation的几种形式
    %基于内容、特征的explanation：利用用户a感兴趣的特征和商品b所拥有的特征来匹配。用户对推荐系统的满意度和信任度与解释高度相关。形式有雷达图等。
    %基于文本的句子形式explanation：在评论等数据中获得更加完善的用户倾向，生成文本句子作为解释。情感抽取工具Sentires（toolkit是一个jre，已得到，未运行），可抽取feature-Opinion-sentiment三元组
\bibitem{Herlocker2000Explanation} Herlocker J L, Konstan J A, Riedl J. Explaining collaborative filtering recommendations[C]// Acm Conference on Computer Supported Cooperative Work. 2000:241-250.
    %为了证明explanation facilities 能提高推荐系统的acceptance，本文通过对210个MovieLens用户的调查，发现绝大部分用户希望在推荐结果中加入explanation。
    %
\bibitem{Ferwerda2012ContentCorrelate} Ferwerda B, Swelsen K, Yang E. Explaining Content-Based Recommendations[J]. Bruceferwerda Com.
    %这篇只发表在作者自己的网站上，但是有被引用。内容是选择过多时，用户满意度会下降。这篇文章通过实验证明，用户的满意度和解释性有关。
    %
\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
    %开发了一个情感抽取工具Sentires，在短语这个级别层面上做情感极性标注。可以从某个产品领域的产品评论中抽取“feature-oppion-sentiment”这样的三元组。例如，在手机领域，“noise-high-negative”，“screen-clear-positive”等。
    %对于我们的大众点评数据，也可以“feature-opinion-sentiment”。其中feature表示52个标签，opinion表示评分，sentiment表示根据评分是积极or消极（与feature其实无关）
\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017.
    %提出了一个LSTM模型来生成评论。并提出八个评估生成文字可读性的测量标准
\bibitem{}
    %
    %
\bibitem{}
    %
    %
\bibitem{}
    %
    %
\bibitem{}
    %
    %
\end{thebibliography}
\end{document}

### 2018-10-27 paper.tex
10-27

@@
 \subsection{motivation}
-Urban computing is defined by Zheng et al.
-~\cite{Zheng2014UrbanConcepts} as an concept where many factors ,such as sensors,prople,vehicles and so on, consist of a dynamic urban system.The aims of urban computing include improve the life level of residents,optimizing urban planning, decreasing traffic jams, reducing various pollution and so on.
-With the improvement of living life of urban residents,GPS-embedded taxi begin to play an important part of urban computing.And the data of taxi mobility provide us an valuable way to compute urban system.For example,Zheng et al.
+Urban computing~\cite{Zheng2014UrbanConcepts} is defined as a concept where many factors ,such as sensors,prople,vehicles and so on, consist of a dynamic urban system. %?
+The aims of urban computing include improving the living quality of residents, optimizing urban planning, decreasing traffic jams, reducing various pollution and so on.
+With the improvement of living life of urban residents, GPS-embedded taxi begin to play an important part of urban computing. 
+And the data of taxi mobility provide us an valuable way to compute urban system.For example,Zheng et al.
 ~\cite{Zheng2011taxicabs} detect the flaws in the existing urban planning of a city using the GPS trajectories of taxis traveling in the urban areas.
-Meng et al.\cite{Meng2017Traffic} propose a framework to infer the city-wide traffic volume information with loop detectors and taxi trajectories.Garg et al.\cite{Garg2018Route}minimizing distance through Monte Carlo tree search to decrease the rate of empty carrying and improve taxi drivers’ profits.
+Meng et al.\cite{Meng2017Traffic} propose a framework to infer the city-wide traffic volume information with loop detectors and taxi trajectories.
+Garg et al.\cite{Garg2018Route}minimizing distance through Monte Carlo tree search to decrease the rate of empty carrying and improve taxi drivers’ profits.
 As you can see, Urban computing is closely linked with urban life.
 
-Discovering regions of different function is a step towards urban computing.In this direction,Yuan et al.~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion,Yuan2018FunctionRegion} do well in discovering regions of different functions %3 references.
+Discovering regions of different function is a step towards urban computing.In this direction, Yuan et al.~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion,Yuan2018FunctionRegion} do well in discovering regions of different functions %3 references.
 %~\cite{Yuan2012FunctionRegion}~\cite{Yuan2015FunctionRegion}:latent activity trajectories~\cite{Yuan2018FunctionRegion}
+% reference
+without explanation
 
-\subsection{explain power}
-%Previous model
-The approaches to explanation recommendation system was developing recently.At the early time,the fundamental methods of personal recommendation is recommendation systems with user-based and item-based.
-Resnick et al.\cite{Resnick1994UserBased} found user-based collaboration filtering recommendation system.The explanation is the similar neighbors whose interests and rates tend to be consistent with target user.Analogously,Sarwar et al.
-\cite{Sarwar2001ItemBased} proposed the recommendation with item-based could find the suitable items which has similar features with purchased items.
+%+figure
 
-%model complex, deep model
-Variants of these basic model constitute the majority of explanation recommendation systems.e.g.,Pazzani et al.\cite{Pazzani2007ContentBased}
-As time going
-
-%data heterogenous 
-%explainability -> disadvantage
-
+syst
 %Explaining the result is of crucial importance
@@
 Our goal is to proposed a model to predict taxi destination and provide persuasive explanation for it.
+input: mobility data
+output: identify urban region, label temporal function of region, explain function aspect-opinion-sentiment
 %Furthermore, provide xxx explaination, activity , focus on aspects
@@
 previous research
+aspect urban related
 
@@
 %second challenge: time bins
+urban region : function temporal 
+mobility data temporal information not fully utilized
 
@@
 
-\subsection{paper structure}
 The remainder of the paper is organized as follows. 

### 2018-10-30 paper.tex
Add files via upload
Introduction和Related work

@@
 \usepackage{graphicx}
+\usepackage{subfigure}
 
@@
 
-\keywords{Explanation  \and Urban computing \and Sentiment analysis.}
+\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis.}
 \end{abstract}
@@
 \subsection{motivation}
-Urban computing~\cite{Zheng2014UrbanConcepts} is defined as a concept where many factors ,such as sensors,prople,vehicles and so on, consist of a dynamic urban system. %?
-The aims of urban computing include improving the living quality of residents, optimizing urban planning, decreasing traffic jams, reducing various pollution and so on.
-With the improvement of living life of urban residents, GPS-embedded taxi begin to play an important part of urban computing. 
-And the data of taxi mobility provide us an valuable way to compute urban system.For example,Zheng et al.
-~\cite{Zheng2011taxicabs} detect the flaws in the existing urban planning of a city using the GPS trajectories of taxis traveling in the urban areas.
-Meng et al.\cite{Meng2017Traffic} propose a framework to infer the city-wide traffic volume information with loop detectors and taxi trajectories.
-Garg et al.\cite{Garg2018Route}minimizing distance through Monte Carlo tree search to decrease the rate of empty carrying and improve taxi drivers’ profits.
-As you can see, Urban computing is closely linked with urban life.
+%urban computing
+Urban computing, defined in~\cite{Zheng2014UrbanConcepts} as a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces.%definition
+One of the most important data source is human mobility data, e.g. pick-ups and drop-offs of taxicabs.
+Such mobility data can contribute to improve living quality of residents, e.g.
+optimizing urban planning~\cite{Zheng2011taxicabs}, easing traffic congestion~\cite{Meng2017Traffic}, decreasing energy consumption ~\cite{Zhang2015Fuel}, reducing air pollution~\cite{Shang2014Pollution} and so on.
+Therefore, mining and modeling mobility data has attracted attentions from both academia and industry.
 
-Discovering regions of different function is a step towards urban computing.In this direction, Yuan et al.~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion,Yuan2018FunctionRegion} do well in discovering regions of different functions %3 references.
-%~\cite{Yuan2012FunctionRegion}~\cite{Yuan2015FunctionRegion}:latent activity trajectories~\cite{Yuan2018FunctionRegion}
-% reference
-without explanation
+%region function
+Identifying functional regions has been a critical step towards efficient government administration and policy making for decades.
+In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
+Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
+Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
+Later work focuses on city-level functional region identification, where a functional region is a region in a city which supports different needs of people’s urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+To obtain accurate identification, recent research tends to use complex models for various form of data,
+e.g. DRoF based on Dirichlet Multinomial
+Regression with latent factors applying in mobility data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}, clustering algorithms based on the 'modularity function'~\cite{Newman2004ModularityFunction} applying in telecommunication~\cite{Ratti2010Telecom},unsupervised semantic labeling framework based on the Latent Dirichlet Allocation applying in remote-sensor data~\cite{Vatsavai2010Remote}.
+%complex model
 
-%+figure
-
-syst
-%Explaining the result is of crucial importance
-We can see that early recommendation systems tend to base on intuition and full with common sense,which improve users' satisfaction easily.
-Now the explanation recommendation systems is developing with more accuracy , which generate more satisfying results.Nevertheless ,the complexity of models is increasing at the meantime,which covers the intuition of whole structure and weakens the persuasiveness of models.So the explanation is playing an important part in recommendation systems.%~\cite{{Zhang2018SIGIR}}
-Majority of users trust and choice satisfaction were highly correlated with the reliability of the explanations for recommendations.Herlocker et al.~\cite{Herlocker2000Explanation}  do an investigation which shows that explanation facilities can improve the acceptance of recommendation systems.The following experiments,e.g.,by Ferwerda et al.~\cite{Ferwerda2012ContentCorrelate} has proven the conclusion.We aim to propose models to explain the destination why we recommend it more persuasively
+%explainability
+Explanation is regarded as a reason or justification given for an action or a plan.
+Majority of trustiness and satisfaction were highly correlated with the reliability of the explanations~\cite{Herlocker2000Explanation}.
+The complex nature of these models covers the intuition explanation of the system,which weakens the interpretability to end users and system designers.%The lack of explanation of the identification xxx
+To fit with the growth of complex models,there is an emerging trend in studying explainable AI~\cite{Preece2018ExplainAI}.
+For example,graph and text with templates explanation is provided in navigation~\cite{Korpan2017navigation} and cognitive cities~\cite{Jose2018cognitive} to improve trustiness of people.%explainable AI reference, data mining
+%Interpretable fuzzy systems have already successfully contributed to build explainable AI systems for cognitive cities.
+%the report combines both NL texts and graphs with the aim of maximizing interpretability.
+To the best of our knowledge, none of the previous urban functional identification provide explanation for the results of region segmentation and functional labels automatically.
+To make the result more convinced,we aim to propose models to explain the identification of urban functional explanation.
 
 %explain implementation, we need to incorporate activity and online sentiment
-Our goal is to proposed a model to predict taxi destination and provide persuasive explanation for it.
-input: mobility data
-output: identify urban region, label temporal function of region, explain function aspect-opinion-sentiment
-%Furthermore, provide xxx explaination, activity , focus on aspects
+In this paper,our goal is to proposed a model to explanation for our functional region clustering results.
+We have two data sets.
+One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
+And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
+We combined the urban computing using mobility data with sentiment analysis using geo-content.
+Fig.\ref{explanation-example} reveal an example of our output of model.
+%Furthermore, provide xxx explanation, activity , focus on aspects
 
+%input
+%output
 \begin{figure}
 \centering
-    \includegraphics[scale=0.25]{Structure.png}
-    \caption{The general structure of our paper}
-    %\label{fig:my_label}
+\subfigure[An example of our identification result]{
+\label{real-map} %% label for first subfigure
+\includegraphics[width=2in]{example-net.png}}
+\hspace{0.1in}
+\subfigure[moving patterns]{
+\label{patterns} %% label for second subfigure
+\includegraphics[width=2in]{example-line.png}}
+\subfigure[POIs in region I]{
+\label{POI} %% label for second subfigure
+\includegraphics[width=2in]{example-POIs.png}}
+\subfigure[Sentiment labels with their probability]{
+\label{sentiment} %% label for second subfigure
+\includegraphics[width=2in]{example-sentiment.png}}
+\caption{The explanation provided for functional region identification.
+Region I in Fig.\ref{real-map} is labeled as commercial region.
+Fig.\ref{patterns} revealed the mobility patterns in the region,which weekends and evenings has more patterns than work time.
+Fig.\ref{POI} shows that there is more shops than other POIs within this region.And from fig.\ref{sentiment} we find that people have a positive sentiment in traffic(label 18) and a negative sentiment in noise(label 25).}
+\label{explanation-example} %% label for entire figure
 \end{figure}
 
-\subsection{problem}
-For solve the problem,we face two challenges.One of it is...and the other is ...
-segment regions = group regions with similar functions
+\subsection{challenge}
+In order to solve the problem,we face two challenges.
 
-function = distribution of activitys and opinions
+The first one of it is to extract the urban feature from comment data.Urban feature is a set of attributes that could describe characters of the Corresponding region,e.g.
+traffic,noise,neighbors and so on.
+Part of our content data comes from social media without detailed coordinates.They are full of sentiment tendencies but have difficulty to induced to a particular region.
+The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.Due to the case,existing sentiment extraction model Sentires~\cite{Zhang2015Sentires} are infeasible in our models.%urban feature
+In order to get the location information from these content data,we....
 
-%challenge
+And the second challenge is that find the function of region is changing with time.The former research regarded time as a distinctive attribute of the region,put it as an input of DRoF model instead of describe its change~\cite{Yuan2012FunctionRegion}.%zheng 's time
 
-previous research
-aspect urban related
+%function = distribution of activitys and opinions
+
+%previous research
 
@@
 
-%second challenge: time bins
-urban region : function temporal 
-mobility data temporal information not fully utilized
-
-\subsection{contribution}
 Our paper has an outstanding result in following several aspect:
 \begin{itemize}
-  \item According to what I have learned,we are the first one to state-of-the-art
-  \item 2
-  \item 3
+  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of user.
+  \item We combined the sentiment and human mobility as explanation,find the urban feature within a region.
+  %\item 3
 \end{itemize}
@@
 
-Two lines of work are related to this paper: sentiment analysis into human mobility,content from social media also provide great help for us.
-Many scholars have made fundamental contributions,and we combined them to find interesting patterns and extended the application .
-
-To the best of our knowledges,we are the first to combined the sentiment into human mobility.
+Two lines of work are related to this paper: urban computing and online sentiment analysis .
 
@@
 Urban computing~\cite{Zheng2014UrbanConcepts} tackles the major issues that cities face by analyzing human mobility collected from different sensors.
-Major sources of human mobility data are checkins in POI~\cite{}, pick-up and drop-off behavior of taxicabs~\cite{} in different locations and  trajectories~\cite{}.
+Major sources of human mobility data are check-ins in POI~\cite{Gallegos16happier}, pick-up and drop-off behavior of taxicabs~\cite{Ge2011TaxiBusiness,Meng2017Traffic} in different locations and  trajectories.
+
 %extract the different among these data
-For checkins data, the most commonly adopted model is.
-For taxicabs data, to fully utilize pick-up and drop-off, xxx is adopted to enhance xxx
-For trajectory data, as it involves multiple points
+The simplest form of mobility data is check-ins data, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
+Statistical association analysis is commonly conducted on check-ins.
+For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
+A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers’ refueling decision~\cite{Zhang2015Fuel}.
+
+The second form of mobility data is origin-destination pairs, i.e. a pick-up point and a drop-off point of a taxi trajectory.
+Clustering methods including Newman modularity cluster algorithm~\cite{Newman2004ModularityFunction} are applied in functional region identification~\cite{Ratti2010Telecom}.
+Recently, latent factor models are proposed to treat a region as document and infer functional-specific ~\cite{Yuan2012FunctionRegion}.%
+Latent activity is imported in topic model in~\cite{Yuan2015FunctionRegion} to define the specific functions of different regions.
+
+Alternatives for origin-destination pairs are trajectory data.
+Applications on trajectory data include recommendation, e.g.
+to recommend more suitable place to drivers~\cite{Ge2011TaxiBusiness,Garg2018Route} and traffic planning, e.g.
+to find reachable region within a given temporal period~\cite{Wu2017Reachable}, %find a fast route
+or to predict travel time~\cite{Wang2018Deep}.
 
 %tasks
-The aim of mobility mining is to uncover informative patterns of improve incomes of taxi drivers~\cite{}, attracts an increasing research interest~\cite{}. 
 However, existing urban computing systems extensively rely on complex machine learning algorithms hence they act as blank-boxes for end users.
-The lack of explainability weakens the persuasiveness and trustworthiness of the system for users
-Our work is to provide intuitive explanations of the results for users or system designers
-%most of them adopt a topic model, treating mobility patterns as words~\cite{}%topic models
+The lack of explanation weakens the persuasiveness and trustworthiness of the system for users.
+Our work is to make up for this drawback by providing intuitive explanations of the results for users or system designers
 
@@
 
-Recently, an emrging research interest is witnessed in exploring the geographical factors that affect online sentiment.
-Empirical studies have been conducted on large-scale human mobility data, such as checkins~\cite{}, trajectory, xxx~\cite{}
-Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{milan15},a high check-in density region usually presents a more positive moode~\cite{},
+Recently, an emerging research interest is witnessed in exploring the geographical factors that affect online sentiment.
+Empirical studies have been conducted on large-scale human mobility data, such as check-in ~\cite{Gallegos16happier}and trajectory~\cite{González2008Track},to find the geographical content analysis with sentiment.
+Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{Alshamsi15milan},a high check-in density region usually presents a more positive mode~\cite{Gallegos16happier}, the whole process and development of a organized movement could be tracked on the social media~\cite{Alvarez2015Movement} and so on.
 
+%and emotion
 %complete survey
@@
 \section{Experiments}
-
 \subsection{Data Set}
@@
     %利用GPS轨迹检测出现有城市规划中存在的缺陷。结果包括：1）存在显著交通问题的区域对，2）连接结构以及它们之间的相关性。这些结果可以评估所实施的规划的有效性，例如一个城市新建的公路和地铁线路，并提醒城市规划者在构思未来规划时没有认识到的问题。
-\bibitem{Meng2017Traffic} Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y.
+\bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y.
 City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories.
@@
     %提出了一个框架来推断城市交通流量信息与环路探测器和出租车轨迹。
+
+\bibitem{Vatsavai2011Remote}Vatsavai R R, Bright E, Varun C, et al.
+Machine learning approaches for high-resolution urban land cover classification:a comparative study[C]// International Conference and Exhibition on Computing for Geospatial Research \& Application, Com.geo 2011, Washington, Dc, Usa, May.
+DBLP, 2011:1-10.
+    %利用遥感数据生成主题地图
+\bibitem{Vatsavai2010Remote}Vatsavai R R, Cheriyadat A, Gleason S.
+Unsupervised Semantic Labeling Framework for Identification of Complex Facilities in High-Resolution Remote Sensing Images[C]// IEEE International Conference on Data Mining Workshops.
+IEEE Computer Society, 2010:273-280.
+    %利用遥感数据生成主题地图
+
+\bibitem{Ratti2010Telecom}Ratti C, Sobolevsky S, Calabrese F, et al. Redrawing the Map of Great Britain from a Network of Human Interactions[J]. Plos One, 2010, 5(12):e14248.
+    %利用电信数据库来划分地图。
+\bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
+\bibitem{Ge2011TaxiBusiness}Ge Y, Liu C, Xiong H, et al.
+A taxi business intelligence system[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, San Diego, Ca, Usa, August.
+DBLP, 2011:735-738.
+    %利用轨迹点来提升司机收入
+\bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp
+    %对之前的functional region做了一个总结。
 \bibitem{Garg2018Route}Garg, N.; Ranu, S.
@@
     %通过Minimizing Distance through Monte Carlo Tree Search来对出租车司机进行路线推荐，使其提高效率，降低空载率。
+\bibitem{Goddard1970EarliestFunction}Goddard J B.
+Functional Regions within the City Centre: A Study by Factor Analysis of Taxi Flows in Central London[J].
+Transactions of the Institute of British Geographers, 1970, 49(49):161-182.
+    %最早提出用出租车轨迹来做功能区划分。但是早期数据都来自司机填写调查问卷，不够准确且数据较小，因此研究的东西比较初步，只能表明伦敦中心区包含许多具有强大内部联系的非常独立的功能区。
+\bibitem{Karlsson2006FunctionalRegionSummary}Karlsson C, Olsson M. The identification of functional regions: theory, methods, and applications[J]. Annals of Regional Science, 2006, 40(1):1-18.
+    %对现有（2006）的功能区识别方法做了总结，将方法归纳为三类：
+    %（1）基于不同城市核心区之间通勤频率的比较的当地劳动力市场方法
+    %（2）通勤区方法（Killian等。1993年，它建立在现有的城市相互依存的基础上，并衡量地区之间双向通勤联系的强度
+    %(3)无障碍方法，它利用两种无障碍方式：雇主与工人的接触。获得工作机会。
+\bibitem{Newman2004ModularityFunction}Newman M E J. Detecting community structure in networks[J]. European Physical Journal B, 2004, 38(2):321-330.
+    %模块化方法的鼻祖
+\bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
+    %早期的Urban function定义
 \bibitem{Yuan2012FunctionRegion}Yuan J, Zheng Y, Xie X.
@@
 Knowledge \& Data Engineering IEEE Transactions on, 2015, 27(3):712-725.
+    %引入latent activity，对他自己2012的论文做了一个拓展，提高精确度
+\bibitem{Yuan2018FunctionRegion}Yuan N J, Zheng Y, Xie X. Discovering Functional Zones in a City Using Human Movements and Points of Interest[J]. 2018.
+    %对之前functional region工作的一个总结，没有再加入新的提高
+\bibitem{Zhang2015Fuel}Zhang F, Yuan N J, Wilkie D, et al.
+Sensing the Pulse of Urban Refueling Behavior:A Perspective from Taxi Mobility[J].
+Acm Transactions on Intelligent Systems \& Technology, 2015, 6(3):1-23.
+    %提出了一个智能系统，用于利用出租车轨迹、POI、道路网络和在线用户的报告来发现城市加油行为。
+\bibitem{Shang2014Pollution}Shang J, Zheng Y, Tong W, et al. Inferring gas consumption and pollution emission of vehicles throughout a city[J]. 2014:1027-1036.
+    %本文利用车辆轨迹（例如出租车）的GPS轨迹，即时推断出在城市时速路段上行驶的车辆的气体消耗量和污染排放量。
+\bibitem{Wu2017Reachable}Wu G, Ding Y, Li Y, et al. Mining Spatio-Temporal Reachable Regions over Massive Trajectory Data[C]// IEEE, International Conference on Data Engineering. IEEE, 2017:1283-1294.
+    %寻找时空可达区域
     %
-\bibitem{Yuan2018FunctionRegion}Yuan N J, Zheng Y, Xie X. Discovering Functional Zones in a City Using Human Movements and Points of Interest[J]. 2018.
+\bibitem{Wang2018Deep}D Wang,J Zhang,W Cao,J Li,Y Zheng.When Will You Arrive? Estimating Travel Time Based on Deep Neural Networks.In International AAAI Conference on Web and Social Media, 2011.
+    %用深度神经网络来预测旅行时间
     %
-\bibitem{Resnick1994UserBased}Resnick P, Iacovou N, Suchak M, et al.
-GroupLens:an open architecture for collaborative filtering of netnews[C]// ACM Conference on Computer Supported Cooperative Work.
-ACM, 1994:175-186.
-    %提出user-based collaboration filtering
-\bibitem{Sarwar2001ItemBased}Sarwar B, Karypis G, Konstan J, et al. Item-based collaborative filtering recommendation algorithms[C]// International Conference on World Wide Web. ACM, 2001:285-295.
-    %提出item-based collaboration filtering
-\bibitem{Pazzani2007ContentBased}Pazzani M J, Billsus D. Content-based recommendation systems[M]// The adaptive web. Springer-Verlag, 2007:325-341.
-    %提出content-based collaboration filtering    
+\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1–13, 2015
+    %从社交网站上挖掘15M这个运动的组织、形成与爆发
+    %
 \bibitem{Alshamsi15milan}Alshamsi A, Awad E, Almehrezi M, et al. Misery loves company: happiness and communication in the city[J]. Epj Data Science, 2015, 4(1):7.
     %把米兰城区划分成100*100区域，根据社交网络发现情绪积极的region更喜欢和其他积极的region交流。
+\bibitem{Cheng2011Check-in}Z. Cheng, J. Caverlee, K. Lee, and D. Sui. Exploring millions of footprints in location sharing services. In International AAAI Conference on Web and Social Media, 2011.
+    %check-in数据来自整个美国.         用户有周期性的行为模式（weekly），受地理、经济、个人社会地位（粉丝越多地位越高）约束，需要content来更好地理解.引入回转半径来帮助sentiment（实际文本分析还是靠字典）
+\bibitem{González2008Track}González M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
+    %追踪100000名手机用户6个月，人体轨迹表现出高度的时间和空间规律。说是human mobility, 但是数据集是长期轨迹包含很多点
 \bibitem{Gallegos16happier}Gallegos L, Huang A, Huang A, et al.
@@
     %提出了一个LSTM模型来生成评论。并提出八个评估生成文字可读性的测量标准
-\bibitem{}
-    %
-    %
-\bibitem{}
-    %
-    %
-\bibitem{}
-    %
-    %
-\bibitem{}
-    %
-    %
+\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63–72.
+    %explain AI
+\bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator.
+In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
+\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems,2018
 \end{thebibliography}

### 2018-11-01 paper.tex
Add files via upload

@@
 \usepackage{subfigure}
+\usepackage{tikz}
+\usetikzlibrary{fit,positioning}
 
@@
 To obtain accurate identification, recent research tends to use complex models for various form of data,
-e.g. DRoF based on Dirichlet Multinomial
-Regression with latent factors applying in mobility data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}, clustering algorithms based on the 'modularity function'~\cite{Newman2004ModularityFunction} applying in telecommunication~\cite{Ratti2010Telecom},unsupervised semantic labeling framework based on the Latent Dirichlet Allocation applying in remote-sensor data~\cite{Vatsavai2010Remote}.
+e.g.
+latent factor models based on Dirichlet Multinomial Regression are applied on mobility data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}, clustering algorithm based on the 'modularity function' is applied on telecommunication~\cite{Newman2004ModularityFunction,Ratti2010Telecom},unsupervised semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}.
 %complex model
@@
 %explainability
-Explanation is regarded as a reason or justification given for an action or a plan.
-Majority of trustiness and satisfaction were highly correlated with the reliability of the explanations~\cite{Herlocker2000Explanation}.
-The complex nature of these models covers the intuition explanation of the system,which weakens the interpretability to end users and system designers.%The lack of explanation of the identification xxx
-To fit with the growth of complex models,there is an emerging trend in studying explainable AI~\cite{Preece2018ExplainAI}.
-For example,graph and text with templates explanation is provided in navigation~\cite{Korpan2017navigation} and cognitive cities~\cite{Jose2018cognitive} to improve trustiness of people.%explainable AI reference, data mining
-%Interpretable fuzzy systems have already successfully contributed to build explainable AI systems for cognitive cities.
-%the report combines both NL texts and graphs with the aim of maximizing interpretability.
-To the best of our knowledge, none of the previous urban functional identification provide explanation for the results of region segmentation and functional labels automatically.
-To make the result more convinced,we aim to propose models to explain the identification of urban functional explanation.
+A severe drawback of existing research is the lack of explanation for the identifications of functional regions.
+Though existing applications~\cite{Yuan2015FunctionRegion} have achieved high identification accuracy,the complex nature of these models weakens the interpretability to end users and system designers.%The lack of explanation of the identification xxx
+There is an emerging trend in studying explainable AI~\cite{Preece2018ExplainAI}.
+In geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
+To the best of our knowledge, none of the previous urban functional identification provide explanation for the results of region segmentation and functional labels.
 
 %explain implementation, we need to incorporate activity and online sentiment
-In this paper,our goal is to proposed a model to explanation for our functional region clustering results.
-We have two data sets.
+In this paper,to make the results more convinced, we build a system that provides explanations for our functional region clustering results.
+We build our system upon two data sets.
 One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
@@
 We combined the urban computing using mobility data with sentiment analysis using geo-content.
-Fig.\ref{explanation-example} reveal an example of our output of model.
-%Furthermore, provide xxx explanation, activity , focus on aspects
+As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals.
+To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we learn/highlight/assign the sentiment towards typical urban features for each functional region.
+For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region.
+We found that people are most interested on traffic for a commercial region.
+And a residential region usually has sentiment positive on vanishing noise.
 
-%input
-%output
 \begin{figure}
@@
 \label{real-map} %% label for first subfigure
-\includegraphics[width=2in]{example-net.png}}
-\hspace{0.1in}
+\includegraphics[width=2.25in]{example-net.png}}
 \subfigure[moving patterns]{
@@
 \includegraphics[width=2in]{example-line.png}}
-\subfigure[POIs in region I]{
+\subfigure[Sentiment labels with their probability]{
 \label{POI} %% label for second subfigure
 \includegraphics[width=2in]{example-POIs.png}}
-\subfigure[Sentiment labels with their probability]{
+\subfigure[POIs in different functional region]{
 \label{sentiment} %% label for second subfigure
@@
 \caption{The explanation provided for functional region identification.
-Region I in Fig.\ref{real-map} is labeled as commercial region.
-Fig.\ref{patterns} revealed the mobility patterns in the region,which weekends and evenings has more patterns than work time.
-Fig.\ref{POI} shows that there is more shops than other POIs within this region.And from fig.\ref{sentiment} we find that people have a positive sentiment in traffic(label 18) and a negative sentiment in noise(label 25).}
+Region I in Fig.\ref{real-map} is labeled as residential region while II is commercial region.
+Fig.\ref{patterns} revealed differences of the mobility patterns between residential region and commercial region,workdays and weekends.
+Fig.\ref{POI} shows the distribution of POIs within the two regions,e.g. there is more shops in commercial region.
+And from fig.\ref{sentiment} we find that people have a more interest in a positive sentiment in traffic for commercial and pay more attention to noise for residential region.}
 \label{explanation-example} %% label for entire figure
@@
 International World Wide Web Conferences Steering Committee, 2016:569-574.
-    %将其他人的统计方法用于划分区域的签到数据集中，比较得出结论：①签到数据越多的地方积极性越高，消极性越低。②发现在签到数据多的地方签到的用户，活动范围都比较大。可以理解为这个地方比较吸引人，人们愿意走更远的路去这里玩。③结合人口普查的结果，发现签到数据多的地方所居住的居民年龄更大、非西班牙裔人口更多、受教育程度更高
+    %将其他人的统计方法用于划分区域的签到数据集中，比较得出结论：① 签到数据越多的地方积极性越高，消极性越低。②发现在签到数据多的地方签到的用户，活动范围都比较大。可以理解为这个地方比较吸引人，人们愿意走更远的路去这里玩。③结合人口普查的结果，发现签到数据多的地方所居住的居民年龄更大、非西班牙裔人口更多、受教育程度更高
 \bibitem{Zhao2016POI}Zhao S, King I, Lyu M R. A Survey of Point-of-interest Recommendation in Location-based Social Networks[J]. 2016.

### 2018-11-10 paper.tex

@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-15--250 words.
+How to identify different functional regions and give them reliable explanations are the main objectives of this work.
 
-\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis.}
+(15--250 words.)
+
+\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis \and Latent Factor \and Matrix Factorization.}
 \end{abstract}
@@
 \section{Introduction}
-
-\subsection{motivation}
+\textbf{Motivation.}
 %urban computing
@@
 %explain implementation, we need to incorporate activity and online sentiment
-In this paper,to make the results more convinced, we build a system that provides explanations for our functional region clustering results.
+In this paper,to make the results more convincing, we build a system that provides explanations for our functional region clustering results.
 We build our system upon two data sets.
@@
 
-\subsection{challenge}
+\textbf{Challenge.}
 In order to solve the problem,we face two challenges.
 
-The first one of it is to extract the urban feature from comment data.Urban feature is a set of attributes that could describe characters of the Corresponding region,e.g.
-traffic,noise,neighbors and so on.
+The first one of it is to extract the urban feature from comment data.
+Urban feature is a set of characters with special geographical attributes, e.g., traffic, noise, neighbors and so on.
 Part of our content data comes from social media without detailed coordinates.They are full of sentiment tendencies but have difficulty to induced to a particular region.
-The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.Due to the case,existing sentiment extraction model Sentires~\cite{Zhang2015Sentires} are infeasible in our models.%urban feature
-In order to get the location information from these content data,we....
+The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
+Due to the scenario, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
+In order to get the location information from these content data, features with typical urban scene are selected from all features extracted by a toolkit called Sentires~\cite{Zhang2015Sentires}.
+These selected urban feature
 
-And the second challenge is that find the function of region is changing with time.The former research regarded time as a distinctive attribute of the region,put it as an input of DRoF model instead of describe its change~\cite{Yuan2012FunctionRegion}.%zheng 's time
+And the second challenge is how to explain the features.
+If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not persuasively explain the reasons for the identification, or even will not be generated.
 
-%function = distribution of activitys and opinions
-
-%previous research
-
-%opinion
-
+\textbf{Contribution.}
 Our paper has an outstanding result in following several aspect:
@@
   \item We combined the sentiment and human mobility as explanation,find the urban feature within a region.
-  %\item 3
+  \item The explanation is given by latent factor model. We use matrix factorization to decrease the sparseness of matrix.
 \end{itemize}
 
+\textbf{Structure.}
 The remainder of the paper is organized as follows.
 We give an overview for related work in Section 2.
-In Section 3, we introduce our novel models as well as proving their logic.
-Section 4 presents the suprior result in experiments of our models.
+In Section 3, we introduce our novel framework as well as proving their feasibility.
+Section 4 presents the superior result in experiments of our models.
 Finally, we made a conclusion and looked forward to our future work in Section 5.
@@
 %extract the different among these data
-The simplest form of mobility data is check-ins data, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
+The simplest form of mobility data is \textbf{check-ins data}, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
 Statistical association analysis is commonly conducted on check-ins.
@@
 
-The second form of mobility data is origin-destination pairs, i.e. a pick-up point and a drop-off point of a taxi trajectory.
+The second form of mobility data is \textbf{origin-destination pairs}, i.e. a pick-up point and a drop-off point of a taxi trajectory.
 Clustering methods including Newman modularity cluster algorithm~\cite{Newman2004ModularityFunction} are applied in functional region identification~\cite{Ratti2010Telecom}.
@@
 
-Alternatives for origin-destination pairs are trajectory data.
+Alternatives for origin-destination pairs are \textbf{trajectory data}.
 Applications on trajectory data include recommendation, e.g.
@@
 
-\iffalse
-\section{Application}
-Our models have a wide range of application and their value
-\subsection{Billboard}
-Billboard
-\subsection{Trajectory}
-\fi
+\subsection{Explanation for Complex Models}
+
+\section{System Overview}
+We proposed a novel framework to make an explanation for the functional region identification.
+
+\section{Urban Feature Extraction}
+
+\section{Explanation Model}
+%relationship between latent factor model and matrix factorization
+
+$$R=b_u+U^TV+\beta()$$
+
+\subsection{Functional Region Identification}
+
+%clustering
+%input:trajectory
+%output:a matrix of activity-location
+
+\subsection{Preliminary: Latent Factor Model and Matrix factorization}
+
+To identify different functional region,we need to train a model
+
+%what is latent factor
+
+%what is kernel function
+
+kernel function is a method that map low-dimension data into high-dimension data.It
+
+%we plans models to combine latent factor
+
+%what is the target of this model
+
+%what is matrix factorization
+
+%in our framework, what is the detail meaning of latent factorization
+
+\subsection{Preliminary: Kernel Function}
+%what is kernel function
+
+%its application on recommendation system
+
+%how to define out matr
 
@@
 \subsection{Preparation}
+To form the basic region of city,we segment the urban area of city into region units by the major road network and make a map simplification.
+The longitude of map range is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.
+Raster-based model is more computationally efficient and succinct for territorial analysis, which is suitable for our map scenario.
+We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid.
+In the grid, the road network is converted to a binary image, as 1 stands for the road while 0 stands for the blank areas.
+
+The main road data is present in Fig.\ref{raw_map}, including motorway, trunk, primary, secondary, tertiary and their links.
+But the Fig.\ref{raw_map} is full of some unnecessary details, such as the lanes of a road and the overpasses, which disturb the distribution of regions.
+As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process are operated on the original road data to remove these details and simplify the map.
+\begin{figure}
+\centering
+\subfigure[Original segment of city]{
+\label{raw_map} %% label for first subfigure
+\includegraphics[width=1.5in]{chengdu_1.png}}
+\subfigure[After dilation operator]{
+\label{dilation} %% label for second subfigure
+\includegraphics[width=1.5in]{chengdu_2.png}}
+\subfigure[After thinning operator]{
+\label{thinning} %% label for second subfigure
+\includegraphics[width=1.5in]{chengdu_3.png}}
+\caption{The preparation process of road network}
+\label{dilation and thinning} %% label for entire figure
+\end{figure}
 
@@
 \subsection{Evaluation Metrics}
+We evaluate the functional region through two approaches.
+One is the percentage of regions that could find explanation label by our framework; while the other is the quality and accuracy of the explanation given by our framework.
+
+For the first approach, we define the percentage of explainable region as follow:
+$$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$
+
+For the second approach,
 
@@
 \section{Conclusion}
-In this paper , we proposed several models to find the most possible destination region for users and add explanation for it to enhance its persuasiveness.
-The models have improve some extra recognition accuracy ,which have an extra contribution for functional city.
+Function regions identification is an important part of urban computing.
+But the relative research lack of persuasive explanation.
+In this paper, we proposed a novel framework to give persuasive explanation for functional regions identification.
+ %to enhance its persuasiveness.
 
@@
     %对之前的functional region做了一个总结。
-\bibitem{Garg2018Route}Garg, N.; Ranu, S.
-Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!
-Proceedings of the 24th ACM SIGKDD International Conference on Knowledge Discovery \& 38; Data Mining,ACM,2018, 1425-1434
+\bibitem{Garg2018Route}Nandani Garg and Sayan Ranu.
+Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!.
+In KDD ’18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19–23, 2018, London, United Kingdom.
+2018.
     %通过Minimizing Distance through Monte Carlo Tree Search来对出租车司机进行路线推荐，使其提高效率，降低空载率。
@@
     %对截止16年最新的50篇与LSBN和POI相关的顶会论文做了一个总结，不知道能不能用上
-\bibitem{Zhang2018SIGIR} Zhang, Y.; Zhang, Y.; Zhang, M.
-SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018) //The 41st International ACM SIGIR Conference on Research \& 38; Development in Information Retrieval,ACM,2018, 1411-1413
+\bibitem{Zhang2018SIGIR}Yongfeng Zhang, Yi Zhang, and Min Zhang.
+SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018).
+In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR ’18).
+2018.
     %概述了推荐系统中explanation的重要性
-\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. 2018.
+\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. arXiv preprint arXiv:1804.11192. 2018.
     %介绍了推荐系统解释的调查概述和未来新视角。主要看了explanation的几种形式
@@
 \bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
+    Zhang Y, Lai G, Zhang M, et al.
+Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval.
+ACM, 2014:83-92.
     %开发了一个情感抽取工具Sentires，在短语这个级别层面上做情感极性标注。可以从某个产品领域的产品评论中抽取“feature-oppion-sentiment”这样的三元组。例如，在手机领域，“noise-high-negative”，“screen-clear-positive”等。
@@
 In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
-\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems,2018
+\bibitem{Jose2018cognitive}Jose M.
+Alonso, Corrado Mencar.
+Building Cognitive Cities with Explainable Artificial Intelligent Systems.
+In Proceedings of the First International Workshop on Comprehensibility and Explanation in AI \& ML, 2017.
+\bibitem{Lu2011Label}Lu Y, Castellanos M, Dayal U, et al.
+Automatic construction of a context-aware sentiment lexicon:an optimization approach[C]// International Conference on World Wide Web, WWW 2011, Hyderabad, India, March 28 - April.
+DBLP, 2011:347-356.
 \end{thebibliography}

### 2018-11-10 paper.tex

@@
 %explain implementation, we need to incorporate activity and online sentiment
-In this paper,to make the results more convincing, we build a system that provides explanations for our functional region clustering results.
-We build our system upon two data sets.
-One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
+\textbf{Our Framework.}
+In this paper,to make the results more convincing, we build a system that provides explanations for functional region clustering results.
+The system is built upon two data sets.
+One is mobility data including 3 million pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
 And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
@@
 \label{real-map} %% label for first subfigure
-\includegraphics[width=2.25in]{example-net.png}}
+\includegraphics[width=1.5in]{example-net.png}}
 \subfigure[moving patterns]{
 \label{patterns} %% label for second subfigure
-\includegraphics[width=2in]{example-line.png}}
-\subfigure[Sentiment labels with their probability]{
-\label{POI} %% label for second subfigure
-\includegraphics[width=2in]{example-POIs.png}}
+\includegraphics[width=1.4in]{example-line.png}}
 \subfigure[POIs in different functional region]{
 \label{sentiment} %% label for second subfigure
-\includegraphics[width=2in]{example-sentiment.png}}
+\includegraphics[width=1.4in]{example-sentiment.png}}
 \caption{The explanation provided for functional region identification.
@@
 We proposed a novel framework to make an explanation for the functional region identification.
+\begin{figure}[h]
+  \centering
+  \includegraphics[scale=0.3]{overview.png}
+  \caption{The overview structure of our framework}
+\end{figure}
 
@@
 
-\subsection{Preliminary: Latent Factor Model and Matrix factorization}
+\subsection{Latent Factor Model and Matrix factorization}
 
@@
 
-\subsection{Preliminary: Kernel Function}
+\subsection{Model:Kernel Function}
 %what is kernel function
@@
 And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.
+\begin{table}[h]
+\caption{Statistics of datasets}\label{dataset}
+\begin{tabular}{|l|l|l|}
+\hline
+Datasets &  attributes & Value\\
+\hline
+comments & shops with coordinates(POI) & \\
+ & shops with comments & \\
+ & total comments & \\
+\hline
+taxicabs & effective orders & 7065937\\
+ & effective days & 30 \\
+\hline
+road networks & geographical scope & [103.93$^\circ$E,104.21$^\circ$E] and [30.56$^\circ$N,30.79$^\circ$N]\\
+ & \#road segments & 3589\\
+ & percentage of major roads & 24.9\%\\
+ & segmented regions & \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process are operated on the original road data to remove these details and simplify the map.
-\begin{figure}
+\begin{figure}[h]
 \centering

### 2018-11-22 paper.tex

@@
 \documentclass[runningheads]{llncs}
+\usepackage{bm}
+\usepackage{CJK}
 \usepackage{graphicx}
@@
 \begin{abstract}
-How to identify different functional regions and give them reliable explanations are the main objectives of this work.
+Functional region identification is a critical step towards Urban computing.
+The state-of-the-art Dirichlet Multinomial Regression(DMR) has identify regions with different function based on topic cluster modeling.
+Due to the ingenious structure inside the complex model, its result is beyond the direct comprehension of humans.
+How to give them reliable explanations are the main objectives of this work.
+To improve the persuasiveness of its result, we proposed a post hoc framework to make explanation for it.
+Optimal latent factor model was applied as explanation after the identification.
+We use matrix factorization to get latent factors and correlate latent factors with urban feature.
+The selected urban feature can be labeled as the explanation.
+Our framework can give an strong evidence to the identification and enhance the satisfaction of users and system designers.
 
@@
 
-\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis \and Latent Factor \and Matrix Factorization.}
+\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis \and Latent Factor \and Post hoc.}
 \end{abstract}
@@
 \section{Introduction}
-\textbf{Motivation.}
 %urban computing
@@
 
+\textbf{Motivation.}
 %explainability
@@
 %explain implementation, we need to incorporate activity and online sentiment
-\textbf{Our Framework.}
+\textbf{Framework.}
 In this paper,to make the results more convincing, we build a system that provides explanations for functional region clustering results.
 The system is built upon two data sets.
-One is mobility data including 3 million pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
-And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
-We combined the urban computing using mobility data with sentiment analysis using geo-content.
+One is mobility data including more than 3 million pick-up and drop-off coordinates and timestamps,which provide fuzzy flow increment of each region units and each time bins.
+The increment, also called moving patterns, are the first input of topic-model-based DMR models as well as POIs.
+Dirichlet Multinomial Regression(DMR) identify the segmented region units as different functions.
+Meanwhile, comment data of shop show the sentiment relavitity between urban feature and the activity that shop related to.
+We pick labels with highest information entropy as urban features from all extracted features.
+Finally, we optimal latent factor with temporal dimension to get a location-feature matrix.
+
 As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals.
-To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we learn/highlight/assign the sentiment towards typical urban features for each functional region.
+To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.
 For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region.
@@
 \textbf{Challenge.}
-In order to solve the problem,we face two challenges.
+In order to solve the problem, we face two challenges.
 
 The first one of it is to extract the urban feature from comment data.
-Urban feature is a set of characters with special geographical attributes, e.g., traffic, noise, neighbors and so on.
-Part of our content data comes from social media without detailed coordinates.They are full of sentiment tendencies but have difficulty to induced to a particular region.
-The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
-Due to the scenario, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
-In order to get the location information from these content data, features with typical urban scene are selected from all features extracted by a toolkit called Sentires~\cite{Zhang2015Sentires}.
-These selected urban feature
+Urban feature is a set of characters with special geographical attributes, e.g., clothes, school, bars and so on.
+Most of our content data are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
+Therefore, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
+In order to get the location information from these content data, all features are extracted as~\cite{Zhang2015Sentires}.
+We select typical features with a high frequency and high information entropy from it.
 
 And the second challenge is how to explain the features.
-If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not persuasively explain the reasons for the identification, or even will not be generated.
+If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not have a strong explanation power for the identification, or even will not be generated.
+To improve the explanation power of our framework, we extract related urban feature and find the corresponding sentiment score between activity and urban feature from contents.
+With the probability that region units belong to which function generated by DMR, we can applied matrix factorization to find the relativity between region units and latent factor, i,e urban feature.
+The urban feature with highest relativity make an explanation for why corresponding region units are identified as such function.
 
@@
 \begin{itemize}
-  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of user.
-  \item We combined the sentiment and human mobility as explanation,find the urban feature within a region.
-  \item The explanation is given by latent factor model. We use matrix factorization to decrease the sparseness of matrix.
+  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of users and urban system designers.
+  \item After identify different functions, We use the contents with sentiment to find the typical urban feature within a region and make explanation.
+  \item The explanation is given by latent factor model. We appplied matrix factorization to get the correlation coefficients between single region units and its features.
 \end{itemize}
@@
 We give an overview for related work in Section 2.
-In Section 3, we introduce our novel framework as well as proving their feasibility.
-Section 4 presents the superior result in experiments of our models.
-Finally, we made a conclusion and looked forward to our future work in Section 5.
+In Section 3, we give an overview of our framework.
+Section 4 shows the process of functional region identification as well as urban feature extraction.
+And Section 5 introduces the post hoc explanation model.
+We test the framework on our datasets and presents the superior explanation result in Section 6
+Finally, we made a conclusion and looked forward to our future work in Section 7.
 
 \section{Related Work}
-
-Two lines of work are related to this paper: urban computing and online sentiment analysis .
+Our work is build upon taxicabs trajectory and comment text.
+With the data source, two lines of work are related to this paper: urban computing and online sentiment analysis .
 
@@
 
-\subsection{Explanation for Complex Models}
+\section{System Overview}
+The section make an overview introduction for our post hoc framework to explain the functional region identification.
+The whole structure is illustrated in Figure ~\ref{overview} while the corresponding steps as follow:
 
-\section{System Overview}
-We proposed a novel framework to make an explanation for the functional region identification.
 \begin{figure}[h]
@@
   \includegraphics[scale=0.3]{overview.png}
+  \label{overview}
   \caption{The overview structure of our framework}
@@
 
-\section{Urban Feature Extraction}
+\emph{1.Functional region identification:}
+
+The input data of first step is taxicabs OD pairs and POIs with coordinates.
+We can get an activity-region matrix with value of the probability that each single region units belong to each activity by DMR.
+And for the region, an activity with highest probability can be output as the function of this region.
+
+\emph{2.Urban feature extraction:}
+
+This step based upon the comments of different shops and activity-region matrix output in last step.
+We select nouns with high frequency and low information entropy as our urban features.
+Meanwhile, the sentiment analyse between urban feature and different activity is also illustrated in an activity-feature matrix.
+
+\emph{3.Train Matrix Factorization model:}
+
+With the certain activity-region matrix $\bm{r}$ and activity-feature matrix $\bm{u}$, we performed an matrix factorization model in form of Equation \ref{model} to get the region-feature matrix $\bm{v}$.
+Training data comes from the given result of step 1 and step 2.
+
+\emph{4.Output label explanation:}
+
+The region-feature matrix $\bm{v}$ generated in step 3 in the input of this step
+For each single region units,we can pick the urban features with highest sentiment score in $\bm{v}$.
+These urban feature is the explanation for the functional region identification.
+
+\section{Urban Feature}
+\subsection{Functional Region Identification}
+A city was segmented into single region units, which is regarded as documents with various themes in topic modeling.
+DMR~\cite{Mimno2012DMR} was applied in functional region identification as explained in~\cite{Yuan2012FunctionRegion}.
+DMR, whose structure is illustrated in Figure~\ref{DMR_ori}, is a topic clustering model based on Latent Dirichlet Allocation(LDA).
+It input some metadata, e.g. authors and publishers, in addtion to basic LDA, which make the topic modeling more accurate.
+As describe in~\cite{Yuan2012FunctionRegion},we regard flow increment calculated in regions as vocabulary in documents, which is marked as $m_{r,n}$ in Figure~\ref{DMR_ori}.
+And POI located in different region units are correlate to the matadata of document, which is marked as $x_r$ in Figure~\ref{DMR_ori}.
+\begin{figure}[h]
+  \centering
+  \includegraphics[scale=0.4]{DMR.png}
+  \caption{The structure of DMR}
+  \label{DMR_ori}
+\end{figure}
+
+\subsection{Urban Feature Extraction}
+To get proper urban features for explaining different functions, we thought that urban features should be nouns with high frequency and low information entropy.
+
+Considering the property of urban features, we separate comment sentences into single words and select all nouns of it.
+With the help of coordinates, these words can correspond to different single units.
+Take the sparseness of latent factor into account, we thought the words had better appear in more region units.
+And we filer the high-frequency nouns as features.
+If the frequency of a word is high enough, i.e. the shops commented with this word is much than a threshold $t$, we thought its frequency is high.
+We set the threshold $t$ as 500.
+
+Meanwhile, to make the urban features more distinguishing, we calculate the information entropy of words for different functional regions generated in Section 4.1.
+Information entropy can measure the amount of information that a word contains.
+Stronger distinguishing ability of a word takes lower information entropy.
+The information entropy is defined as:
+$$H[x_i,word_j] = -\sum_i p(x_i,word_j)\log p(x_i,word_j)$$
+where $x_i$ stands for $i$th functional regions;
+$p(x_i,word_j)$ is the proportion of shops located in $i$th functional regions commented with $j$th word in all shops located in $i$th functional regions.
+We select features with lowest information entropy as our urban features, which are shown in Table \ref{urbanfeatures}.
+
+\begin{table}[h]
+\centering
+\caption{Selected Urban Features}
+\label{urbanfeatures}
+\begin{tabular}{c|c|c|c|c}
+\hline
+features &  Alley & Brand & Center & Square\\
+\hline
+information entropy &  &  &  & \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Urban Feature Matrix}
 
 \section{Explanation Model}
-%relationship between latent factor model and matrix factorization
+In this section,we describe our post hoc framework for explanation in detail.
 
-$$R=b_u+U^TV+\beta()$$
+\subsection{Latent Factor Model}
+A classical model has Intuitive explanation is latent factor model.
+It has a wide application in various fields.
+The form of latent factor applied in recommendation system to predict rating of user $u$ to product $p$ as follow:
+\begin{equation}
+\hat{r}_{u,p}= g+b_u+b_p+\bm{x_u}^T\bm{y_p} \label{basic}
+\end{equation}
+where $g$ is a base rating in the system while $b_u$ and $b_p$ is the bias of user $u$ and product $p$;
+$\bm{x_u}$ and $\bm{y_p}$ denote vectors of latent factors for corresponding user and product.
 
-\subsection{Functional Region Identification}
+The matrix $r$ is rating that user $u$ give to product $p$.
+Correlate users as activities, products as locations, we translated the matrix into the sentiment analysis score that actitivy $a$ to region $l$.
+We can make our matrix based upon this stand latent factor model presented in Equation \ref{basic}.
 
-%clustering
-%input:trajectory
-%output:a matrix of activity-location
+\subsection{Our model}
+Considering the temporal attribute of datesets, ~\cite{Zhang2017Model} has proposed an Historical Influence Aware Latent Factor(HIALF) model take the historical influence into account, which fit our intuition well and make the power of explanation stronger.
 
-\subsection{Latent Factor Model and Matrix factorization}
+Therefore, we define our matrix factorization model as:
+\begin{equation}
+\hat{r}_{l,i,a}=b_l+U_a^TV_l+\beta(e_{a,i})\label{model}
+\end{equation}
+where $\hat{r}_{l,i,a}$ stands for the predicted probability at $i$-th time bin that region $l$ belongs to activity $a$;
+$b_l$ is the bias of region $l$;
+$\bm{U_a}$ and $\bm{V_l}$ represent the latent feature of activity $a$ and region $l$;
+$e_{a,i}$ generated by prior expectation;
+and $\beta(\cdot)$ demonstrates the bias curve changing with $e_{a,i}$.
+Now we describe how to learn the $\beta(x)$ and generate a more realistic prior expectaion $e_{a,i}$.
 
-To identify different functional region,we need to train a model
+\textbf{Modeling the bias curve $\beta(x)$}
+The form of $\beta(x)$ is unknown.
+We can constrain it with a data-driven approach.
+Kernel regression is a kind of typical non-parameter learning and fit the $\beta(x)$ model well.
 
-%what is latent factor
+If we have a set of independent variables $e_l$ and dependent variables $v_l$, and $v_l=\beta(e_l)+\epsilon_l$ where $\epsilon_l$ is the noise from the standard normal distribution, we can defind $\beta(x)$ as:
+$$\beta(x) = \frac{\sum_{k=1}^{n}w(x,e_l)v_l}{\sum_{k=1}^{n}w(x,e_l)}$$
+where $w(x, x_i) = \exp(-\kappa(x-x_i)^2)$ and $\kappa$ is given by 10.
+Actually, $e_l$ is given while $v_l$ is unknown.
+Therefore, we set $e_l$ as several arithmetic progression within data range and $v_l$ is the corresponding unknown parameters so that we can learn them from datasets.
 
-%what is kernel function
+\textbf{Modeling the prior expectation $e_{a,i}$}
+$$e_{a,i} = \frac{\sum_{k=1}^{i-1}\xi(i-k) r_{a,k}}{\sum_{k=1}^{i-1}\xi(i-k)}$$
+where $\xi(d)=\exp(-\gamma\times d)$ is an exponential triggering kernel that models the decrease of histroy influence;
+$\gamma$ controls the degree that history probability influence current probability;
+and $r_{a,k}$ denotes the sentiment of activity $a$ when time bin $k$.
 
-kernel function is a method that map low-dimension data into high-dimension data.It
+\subsection{Model Inference}
+After build a matrix factorization model, we set up objective function as follow:
+\begin{equation}
+F=\sum\limits_{(p,l,u)\in\mathcal{M}}(r_{l,i,a}-\hat{r}_{l,i,a})^2+\lambda_1(b_l^2+||{\bm{y_r}}||_2^2)+\lambda_2(\sum\limits_{l}v_l^2)+\lambda_3(\sum\limits_{\alpha}\alpha_u^2)
+\label{inference}
+\end{equation}
+where $\Theta$ stands for the unknown parameters, $\bm{y_p}$, $b_u$, $\alpha$ and $v_l$.
+$\mathcal{M}$ contains all $(p,l,u)$ pairs, and each pair of it stands for the related parameter of region $l$ belongs to activity $a$ at time bin $i$.
+$r_{r,i,a}$ is the probability generated by DMR while $\hat{r}_{r,i,a}$ is the predicted probability by Equation \ref{model}.
+The first item of Equation \ref{inference} is quadratic sums of the difference between real probability $r_{r,i,a}$ and predected probability $\hat{r}_{r,i,a}$.
+To prevent from overfitting, we three regularization terms and $\lambda_1$, $\lambda_2$ and $\lambda_3$ are given as hyperparameters.
 
-%we plans models to combine latent factor
-
-%what is the target of this model
-
-%what is matrix factorization
-
-%in our framework, what is the detail meaning of latent factorization
-
-\subsection{Model:Kernel Function}
-%what is kernel function
-
-%its application on recommendation system
-
-%how to define out matr
+To get our optimal $\bm{y_r}$, we aim to solve the following optimization problem and make the predicted probability $\hat{r}_{r,i,a}$ as close as possible to the real probability$r_{r,i,a}$:
+$$\min\limits_{\Theta} F$$
+The approach to get it is stochastic gradient descent(SGD) algorithm due to its efficiency in learning the parameter of objective function
 
@@
 The data set for our experiments including both mobility data and content data.
-The mobility data including the pick-up and drop-off time and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
-And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.
+The mobility data including the pick-up and drop-off timestamps and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
+And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping, which helps sentiment analysis of the regions.
 \begin{table}[h]
 \caption{Statistics of datasets}\label{dataset}
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|l|c|}
 \hline
@@
 \hline
-comments & shops with coordinates(POI) & \\
- & shops with comments & \\
- & total comments & \\
+comments & shops with coordinates(POI) & 109686\\
+ & shops with comments & 50853\\
+ & total comments & 3213264\\
 \hline
@@
 road networks & geographical scope & [103.93$^\circ$E,104.21$^\circ$E] and [30.56$^\circ$N,30.79$^\circ$N]\\
- & \#road segments & 3589\\
- & percentage of major roads & 24.9\%\\
- & segmented regions & \\
+ & road segments & 3712\\
+ & percentage of major roads & 54.9\%\\
+ & segmented regions & 901\\
 \hline
@@
 But the Fig.\ref{raw_map} is full of some unnecessary details, such as the lanes of a road and the overpasses, which disturb the distribution of regions.
-As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process are operated on the original road data to remove these details and simplify the map.
+As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process illustrated in Figure~\ref{dilation and thinning} are operated on the original road data to remove some small regions and simplify the map.
 \begin{figure}[h]
@@
 
-\subsection{Baseline and other comparison}
+We use DMR to identify regions into 8/4 types with different regions, which is illustrated in Figure~\ref{DMR_result}
+The main function regions in the city is residence region, business region, study and science region, scenery regions and so on.
+
+\begin{figure}[h]
+\centering
+\subfigure[After dilation operator]{
+\label{thin_result} %% label for second subfigure
+\includegraphics[width=2.3in]{FunctionalRegions_thinning.png}}
+\subfigure[segmented region units of the city]{
+\label{DMR_result} %% label for second subfigure
+\includegraphics[width=2.3in]{FunctionalRegions_DMR.png}}
+\caption{results of DMR}
+\label{The results of functional region identification}
+\end{figure}
 
@@
 
-For the first approach, we define the percentage of explainable region as follow:
+For the evaluation of percentage of explainable region, we put forward the $explanation percentage$ to measure the proportion that regions with explainable labels as:
 $$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$
 
-For the second approach,
+For the second approach,we take a metric to measure the quality and accuracy of our explanation label.
+
+\subsection{Baseline and other comparison}
 
 \subsection{result}
+\begin{table}[h]
+\centering
+\caption{Functional Regions and corresponding urban feature}\label{dataset}
+\begin{tabular}{c|c}
+\hline
+Functions & Urban Feature\\
+\hline
+Business & \\
+\hline
+Residence & \\
+\hline
+Study & \\
+\hline
+Scenery & \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 Function regions identification is an important part of urban computing.
-But the relative research lack of persuasive explanation.
-In this paper, we proposed a novel framework to give persuasive explanation for functional regions identification.
- %to enhance its persuasiveness.
+But its evaluation depend on human intuition and urban planning, which is hard to display in terms of statistics.
+To make up for the lack of persuasive explanation, we proposed a post hoc framework to give persuasive explanation for functional regions identification in this paper.
+Our datasets including over 3 million comments of shops and taxicabs OD pair trajectory in November 2016 generated by more than 7 million orders.
+We utilized the framework to general most relative labels for every single region units as explanation.
+According to the experiments performed in the datasets, our framework give an strong evidence to the identification and enhance its persuasiveness.
+The result can help users and urban system designers easily recognize the region functions, which is helpful in a variety of urban applications, such as urban planning, location choosing for a business advertisement casting, and so on.
+
+There are some directions can improve in the future work.
+First is to full utilize our data sets of trajectory. 
+Our trajectory datasets not only have origin and destination, but also include the detail points that users have passed by.
+There are also some interesting patterns within these process points, and we can find new moving patterns in it. 
+Second, we want to change our phrase-level explanation into sentence-level, which is more similar to natural language.
 
@@
 DBLP, 2011:347-356.
+\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S .
+Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems.
+ACM, 2017.
+\bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
 \end{thebibliography}

### 2018-11-22 paper.tex
1122

@@
 %urban computing
-Urban computing, defined in~\cite{Zheng2014UrbanConcepts} as a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces.%definition
-One of the most important data source is human mobility data, e.g. pick-ups and drop-offs of taxicabs.
-Such mobility data can contribute to improve living quality of residents, e.g.
-optimizing urban planning~\cite{Zheng2011taxicabs}, easing traffic congestion~\cite{Meng2017Traffic}, decreasing energy consumption ~\cite{Zhang2015Fuel}, reducing air pollution~\cite{Shang2014Pollution} and so on.
-Therefore, mining and modeling mobility data has attracted attentions from both academia and industry.
+Urban computing is a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces~\cite{Zheng2014UrbanConcepts}. 
+Recently, urban computing has attracted attentions from both academy and industry.
+One critical step towards efficient urban computing is to identify functional regions, which is a region in a city that supports certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
 
-%region function
-Identifying functional regions has been a critical step towards efficient government administration and policy making for decades.
-In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
-Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
-Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
-Later work focuses on city-level functional region identification, where a functional region is a region in a city which supports different needs of people’s urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
-To obtain accurate identification, recent research tends to use complex models for various form of data,
-e.g.
-latent factor models based on Dirichlet Multinomial Regression are applied on mobility data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}, clustering algorithm based on the 'modularity function' is applied on telecommunication~\cite{Newman2004ModularityFunction,Ratti2010Telecom},unsupervised semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}.
-%complex model
+%related work survey
+Most of previous functional region identification systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}.
+such as origin-destination pairs of labour market data~\cite{Karlsson2006FunctionalRegionSummary}.
+For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}, spectural clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, and DMR (Dirichlet Multinomial Regression) are applied on pick-ups and drop-offs data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
 
-\textbf{Motivation.}
-%explainability
-A severe drawback of existing research is the lack of explanation for the identifications of functional regions.
-Though existing applications~\cite{Yuan2015FunctionRegion} have achieved high identification accuracy,the complex nature of these models weakens the interpretability to end users and system designers.%The lack of explanation of the identification xxx
-There is an emerging trend in studying explainable AI~\cite{Preece2018ExplainAI}.
-In geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
-To the best of our knowledge, none of the previous urban functional identification provide explanation for the results of region segmentation and functional labels.
+%problem of past research
+A severe drawback of existing research is the lack of explanation for functional regions.
+Clustering methods have long been suffering from the subjective issue, i.e. the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means. 
+Furthermore, to obtain accurate identification, recent research tends to use complex models~\cite{Yuan2015FunctionRegion} on a combination of different data sources. 
+The complex nature of these models is an obstacle for people to capture the ``semantics'' of the identification.
+
+%motivation
+Explainable functional region identification is beneficial for both system designers and end users.
+For example, providing explanations help system designers to better intepretate the clustering results and improve the system. 
+The explanations can incubate a series of applications for end users, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on. 
+In a bigger picture, there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}.
+However, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
+
+%goal
+In this paper, we present a novel system for explainable functional region identification.
+The system provides post-hoc explanations, i.e.
+the explanations are not relevant to the identification algorithm.
+Instead, the system attempts to resolve the ``semantics" of cluster labels generated by any functional region identification algorithm by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features and public sentiments for each activity; and (3) listing the most important urban features in the region.
+
+As shown in Fig.\ref{explanation-example}, the city of Chengdu has been functional regions delivers explanations of the  functionals.
+To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.
+For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region.
+We found that people are most interested on traffic for a commercial region.
+And a residential region usually has sentiment positive on vanishing noise.
 
@@
 Finally, we optimal latent factor with temporal dimension to get a location-feature matrix.
-
-As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals.
-To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.
-For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region.
-We found that people are most interested on traffic for a commercial region.
-And a residential region usually has sentiment positive on vanishing noise.
 
@@
 For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
-A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers’ refueling decision~\cite{Zhang2015Fuel}.
+A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers refueling decision~\cite{Zhang2015Fuel}.
 
@@
 
+In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
+Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
+Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
+Later work focuses on city-level functional region identification,
+
 %tasks
@@
 Recently, an emerging research interest is witnessed in exploring the geographical factors that affect online sentiment.
-Empirical studies have been conducted on large-scale human mobility data, such as check-in ~\cite{Gallegos16happier}and trajectory~\cite{González2008Track},to find the geographical content analysis with sentiment.
+Empirical studies have been conducted on large-scale human mobility data, such as check-in ~\cite{Gallegos16happier}and trajectory~\cite{Gonzlez2008Track},to find the geographical content analysis with sentiment.
 Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{Alshamsi15milan},a high check-in density region usually presents a more positive mode~\cite{Gallegos16happier}, the whole process and development of a organized movement could be tracked on the social media~\cite{Alvarez2015Movement} and so on.
@@
 Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.
-    %综述城市计算的概念和框架
+
 \bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
-    %利用GPS轨迹检测出现有城市规划中存在的缺陷。结果包括：1）存在显著交通问题的区域对，2）连接结构以及它们之间的相关性。这些结果可以评估所实施的规划的有效性，例如一个城市新建的公路和地铁线路，并提醒城市规划者在构思未来规划时没有认识到的问题。
+
 \bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y.
@@
 Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10
-    %提出了一个框架来推断城市交通流量信息与环路探测器和出租车轨迹。
 
@@
 DBLP, 2011:1-10.
-    %利用遥感数据生成主题地图
+
 \bibitem{Vatsavai2010Remote}Vatsavai R R, Cheriyadat A, Gleason S.
@@
 IEEE Computer Society, 2010:273-280.
-    %利用遥感数据生成主题地图
 
 \bibitem{Ratti2010Telecom}Ratti C, Sobolevsky S, Calabrese F, et al. Redrawing the Map of Great Britain from a Network of Human Interactions[J]. Plos One, 2010, 5(12):e14248.
-    %利用电信数据库来划分地图。
+
 \bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
@@
 DBLP, 2011:735-738.
-    %利用轨迹点来提升司机收入
 \bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp
-    %对之前的functional region做了一个总结。
+
 \bibitem{Garg2018Route}Nandani Garg and Sayan Ranu.
 Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!.
-In KDD ’18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19–23, 2018, London, United Kingdom.
+In KDD 18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19-23, 2018, London, United Kingdom.
 2018.
-    %通过Minimizing Distance through Monte Carlo Tree Search来对出租车司机进行路线推荐，使其提高效率，降低空载率。
+
 \bibitem{Goddard1970EarliestFunction}Goddard J B.
@@
 Transactions of the Institute of British Geographers, 1970, 49(49):161-182.
-    %最早提出用出租车轨迹来做功能区划分。但是早期数据都来自司机填写调查问卷，不够准确且数据较小，因此研究的东西比较初步，只能表明伦敦中心区包含许多具有强大内部联系的非常独立的功能区。
+
 \bibitem{Karlsson2006FunctionalRegionSummary}Karlsson C, Olsson M. The identification of functional regions: theory, methods, and applications[J]. Annals of Regional Science, 2006, 40(1):1-18.
-    %对现有（2006）的功能区识别方法做了总结，将方法归纳为三类：
-    %（1）基于不同城市核心区之间通勤频率的比较的当地劳动力市场方法
-    %（2）通勤区方法（Killian等。1993年，它建立在现有的城市相互依存的基础上，并衡量地区之间双向通勤联系的强度
-    %(3)无障碍方法，它利用两种无障碍方式：雇主与工人的接触。获得工作机会。
+
 \bibitem{Newman2004ModularityFunction}Newman M E J. Detecting community structure in networks[J]. European Physical Journal B, 2004, 38(2):321-330.
-    %模块化方法的鼻祖
+
 \bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
-    %早期的Urban function定义
 \bibitem{Yuan2012FunctionRegion}Yuan J, Zheng Y, Xie X.
@@
 ACM, 2012:186-194.
-    %套用LDA，根据功能划分城市区域
+
 \bibitem{Yuan2015FunctionRegion}Yuan N J, Zheng Y, Xie X, et al.
@@
 Knowledge \& Data Engineering IEEE Transactions on, 2015, 27(3):712-725.
-    %引入latent activity，对他自己2012的论文做了一个拓展，提高精确度
+
 \bibitem{Yuan2018FunctionRegion}Yuan N J, Zheng Y, Xie X. Discovering Functional Zones in a City Using Human Movements and Points of Interest[J]. 2018.
-    %对之前functional region工作的一个总结，没有再加入新的提高
+
 \bibitem{Zhang2015Fuel}Zhang F, Yuan N J, Wilkie D, et al.
@@
 Acm Transactions on Intelligent Systems \& Technology, 2015, 6(3):1-23.
-    %提出了一个智能系统，用于利用出租车轨迹、POI、道路网络和在线用户的报告来发现城市加油行为。
+
 \bibitem{Shang2014Pollution}Shang J, Zheng Y, Tong W, et al. Inferring gas consumption and pollution emission of vehicles throughout a city[J]. 2014:1027-1036.
-    %本文利用车辆轨迹（例如出租车）的GPS轨迹，即时推断出在城市时速路段上行驶的车辆的气体消耗量和污染排放量。
+
 \bibitem{Wu2017Reachable}Wu G, Ding Y, Li Y, et al. Mining Spatio-Temporal Reachable Regions over Massive Trajectory Data[C]// IEEE, International Conference on Data Engineering. IEEE, 2017:1283-1294.
-    %寻找时空可达区域
-    %
+
 \bibitem{Wang2018Deep}D Wang,J Zhang,W Cao,J Li,Y Zheng.When Will You Arrive? Estimating Travel Time Based on Deep Neural Networks.In International AAAI Conference on Web and Social Media, 2011.
-    %用深度神经网络来预测旅行时间
-    %
-\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1–13, 2015
-    %从社交网站上挖掘15M这个运动的组织、形成与爆发
-    %
+
+\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1-13, 2015
+
 \bibitem{Alshamsi15milan}Alshamsi A, Awad E, Almehrezi M, et al. Misery loves company: happiness and communication in the city[J]. Epj Data Science, 2015, 4(1):7.
-    %把米兰城区划分成100*100区域，根据社交网络发现情绪积极的region更喜欢和其他积极的region交流。
+
 \bibitem{Cheng2011Check-in}Z. Cheng, J. Caverlee, K. Lee, and D. Sui. Exploring millions of footprints in location sharing services. In International AAAI Conference on Web and Social Media, 2011.
-    %check-in数据来自整个美国.         用户有周期性的行为模式（weekly），受地理、经济、个人社会地位（粉丝越多地位越高）约束，需要content来更好地理解.引入回转半径来帮助sentiment（实际文本分析还是靠字典）
-\bibitem{González2008Track}González M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
-    %追踪100000名手机用户6个月，人体轨迹表现出高度的时间和空间规律。说是human mobility, 但是数据集是长期轨迹包含很多点
+
+\bibitem{Gonzlez2008Track}Gonzlez M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
+
 \bibitem{Gallegos16happier}Gallegos L, Huang A, Huang A, et al.
@@
 International World Wide Web Conferences Steering Committee, 2016:569-574.
-    %将其他人的统计方法用于划分区域的签到数据集中，比较得出结论：① 签到数据越多的地方积极性越高，消极性越低。②发现在签到数据多的地方签到的用户，活动范围都比较大。可以理解为这个地方比较吸引人，人们愿意走更远的路去这里玩。③结合人口普查的结果，发现签到数据多的地方所居住的居民年龄更大、非西班牙裔人口更多、受教育程度更高
+
 \bibitem{Zhao2016POI}Zhao S, King I, Lyu M R. A Survey of Point-of-interest Recommendation in Location-based Social Networks[J]. 2016.
-    %对截止16年最新的50篇与LSBN和POI相关的顶会论文做了一个总结，不知道能不能用上
+
 \bibitem{Zhang2018SIGIR}Yongfeng Zhang, Yi Zhang, and Min Zhang.
 SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018).
-In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR ’18).
+In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 18).
 2018.
-    %概述了推荐系统中explanation的重要性
+
 \bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. arXiv preprint arXiv:1804.11192. 2018.
-    %介绍了推荐系统解释的调查概述和未来新视角。主要看了explanation的几种形式
-    %基于内容、特征的explanation：利用用户a感兴趣的特征和商品b所拥有的特征来匹配。用户对推荐系统的满意度和信任度与解释高度相关。形式有雷达图等。
-    %基于文本的句子形式explanation：在评论等数据中获得更加完善的用户倾向，生成文本句子作为解释。情感抽取工具Sentires（toolkit是一个jre，已得到，未运行），可抽取feature-Opinion-sentiment三元组
+
 \bibitem{Herlocker2000Explanation} Herlocker J L, Konstan J A, Riedl J. Explaining collaborative filtering recommendations[C]// Acm Conference on Computer Supported Cooperative Work. 2000:241-250.
-    %为了证明explanation facilities 能提高推荐系统的acceptance，本文通过对210个MovieLens用户的调查，发现绝大部分用户希望在推荐结果中加入explanation。
-    %
+
 \bibitem{Ferwerda2012ContentCorrelate} Ferwerda B, Swelsen K, Yang E. Explaining Content-Based Recommendations[J]. Bruceferwerda Com.
-    %这篇只发表在作者自己的网站上，但是有被引用。内容是选择过多时，用户满意度会下降。这篇文章通过实验证明，用户的满意度和解释性有关。
-    %
+
 \bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
@@
 ACM, 2014:83-92.
-    %开发了一个情感抽取工具Sentires，在短语这个级别层面上做情感极性标注。可以从某个产品领域的产品评论中抽取“feature-oppion-sentiment”这样的三元组。例如，在手机领域，“noise-high-negative”，“screen-clear-positive”等。
-    %对于我们的大众点评数据，也可以“feature-opinion-sentiment”。其中feature表示52个标签，opinion表示评分，sentiment表示根据评分是积极or消极（与feature其实无关）
-\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017.
-    %提出了一个LSTM模型来生成评论。并提出八个评估生成文字可读性的测量标准
-\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63–72.
+
+\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017
+\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63-72.
     %explain AI

### 2018-11-22 paper.tex
1122

@@
 
-\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis \and Latent Factor \and Post hoc.}
+\keywords{Explainable AI  \and Urban computing \and Online Sentiment analysis \and Big data analysis \and Functional region identification}
 \end{abstract}
@@
 %urban computing
-Urban computing is a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces~\cite{Zheng2014UrbanConcepts}. 
+Urban computing is a process to acquire, integrate and analyze big and heterogeneous data generated by diverse sources in urban spaces~\cite{Zheng2014UrbanConcepts}. 
 Recently, urban computing has attracted attentions from both academy and industry.
-One critical step towards efficient urban computing is to identify functional regions, which is a region in a city that supports certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+One critical step towards efficient urban computing is to identify \emph{functional regions}, which are regions in a city that support certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
 
 %related work survey
-Most of previous functional region identification systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}.
-such as origin-destination pairs of labour market data~\cite{Karlsson2006FunctionalRegionSummary}.
-For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}, spectural clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, and DMR (Dirichlet Multinomial Regression) are applied on pick-ups and drop-offs data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+Most of previous \emph{Functional Region Identification} (FRI) systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}.
+For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, variants of Latent Dirichlet Allocation (LDA) is applied on remote-sensor data~\cite{Vatsavai2010Remote} and taxicab pick-ups and drop-offs data~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
 
@@
 A severe drawback of existing research is the lack of explanation for functional regions.
-Clustering methods have long been suffering from the subjective issue, i.e. the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means. 
-Furthermore, to obtain accurate identification, recent research tends to use complex models~\cite{Yuan2015FunctionRegion} on a combination of different data sources. 
-The complex nature of these models is an obstacle for people to capture the ``semantics'' of the identification.
+Clustering methods generate cluster labels that have long been suffering from the subjective issue, i.e.
+the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means.
+Furthermore, to obtain accurate identification, recent research tends to use complex models such as the Dirichlet Multinomial Regression model in~\cite{Yuan2015FunctionRegion} . 
+The complex nature of these models is an obstacle for people to capture the ``semantics'' of the clustering results.
 
 %motivation
-Explainable functional region identification is beneficial for both system designers and end users.
-For example, providing explanations help system designers to better intepretate the clustering results and improve the system. 
-The explanations can incubate a series of applications for end users, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on. 
-In a bigger picture, there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}.
-However, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
+There is a strong incentive to develop explainable FRI system, which \emph{explains} the identification of functional regions. 
+Explainable FRI is beneficial for both system designers and end users.
+For system designers, providing explanations help them better diagnose the system and improve system performance. 
+For end users, explanations not only facilitate interpretation of the clustering results, but also incubate a wide range of applications, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on.
 
 %goal
-In this paper, we present a novel system for explainable functional region identification.
-The system provides post-hoc explanations, i.e.
-the explanations are not relevant to the identification algorithm.
-Instead, the system attempts to resolve the ``semantics" of cluster labels generated by any functional region identification algorithm by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features and public sentiments for each activity; and (3) listing the most important urban features in the region.
+Though there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
+In this paper, we present a novel system for explainable FRI by integrating heterogeneous data sources.
+Our system provides post-hoc explanations, i.e.
+the explanations are not relevant to the FRI algorithm.
+Instead, for an arbitrary FRI algorithm, the system attempts to resolve the ``semantics" of the generated cluster labels by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features for each activity; and (3) listing the most important urban features in the region.
 
-As shown in Fig.\ref{explanation-example}, the city of Chengdu has been functional regions delivers explanations of the  functionals.
-To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.
-For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region.
-We found that people are most interested on traffic for a commercial region.
-And a residential region usually has sentiment positive on vanishing noise.
+%figure ??? real example or made-up example
+As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions.
+For a specific region $r_1$ with label $I$, the system delivers textual and visual descriptions.
+Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from the analysis of mobility data, these two activities bring in $\%$ of the traffic flow to region $r_1$.
+Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews.
+Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system \textbf{explains} why $r_1$ is labeled as $l$.
 
-%explain implementation, we need to incorporate activity and online sentiment
-\textbf{Framework.}
-In this paper,to make the results more convincing, we build a system that provides explanations for functional region clustering results.
-The system is built upon two data sets.
-One is mobility data including more than 3 million pick-up and drop-off coordinates and timestamps,which provide fuzzy flow increment of each region units and each time bins.
-The increment, also called moving patterns, are the first input of topic-model-based DMR models as well as POIs.
-Dirichlet Multinomial Regression(DMR) identify the segmented region units as different functions.
-Meanwhile, comment data of shop show the sentiment relavitity between urban feature and the activity that shop related to.
-We pick labels with highest information entropy as urban features from all extracted features.
-Finally, we optimal latent factor with temporal dimension to get a location-feature matrix.
+%highlight
+We highlight a key property of the proposed system: the power to integrate heterogenous data sources.
+On one hand, explanations essentially involve semantics.
+In our system, the semantics of labels are expressed through urban activities and urban features, which are extracted from online review data.
+On the other hand, the cluster labels are obtained in mobility data.
+To obtain more reasonable explanations that comply with the clustering algorithm, the semantics are blended with moving patterns discovered in mobility data.
+In building such a system, we face two challenges.
 
@@
 
-\textbf{Challenge.}
-In order to solve the problem, we face two challenges.
-
+%manual label costly supervision in sufficient
 The first one of it is to extract the urban feature from comment data.
@@
 
+%unsupervised
+
+%how to embed mobility data
 And the second challenge is how to explain the features.
@@
 The urban feature with highest relativity make an explanation for why corresponding region units are identified as such function.
+
+%bias curve
 
@@
 
-\textbf{Structure.}
 The remainder of the paper is organized as follows.

### 2018-11-23 paper.tex
introduction

@@
 Explainable FRI is beneficial for both system designers and end users.
-For system designers, providing explanations help them better diagnose the system and improve system performance. 
+For system designers, explanations help them better diagnose the system and improve system performance. 
 For end users, explanations not only facilitate interpretation of the clustering results, but also incubate a wide range of applications, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on.
@@
 As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions.
-For a specific region $r_1$ with label $I$, the system delivers textual and visual descriptions.
+For a specific region $r_1$ with label $l$, the system delivers textual and visual descriptions.
 Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from the analysis of mobility data, these two activities bring in $\%$ of the traffic flow to region $r_1$.
 Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews.
-Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system \textbf{explains} why $r_1$ is labeled as $l$.
+Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system explains why $r_1$ is labeled as $l$.
 
 %highlight
-We highlight a key property of the proposed system: the power to integrate heterogenous data sources.
-On one hand, explanations essentially involve semantics.
-In our system, the semantics of labels are expressed through urban activities and urban features, which are extracted from online review data.
-On the other hand, the cluster labels are obtained in mobility data.
-To obtain more reasonable explanations that comply with the clustering algorithm, the semantics are blended with moving patterns discovered in mobility data.
+We highlight a key property of the proposed explainable FRI system: \textbf{the power to integrate heterogenous data sources to offer semantic explanations for mobility patterns}.
+On one hand, explanations essentially involve semantics, which are not available in pure mobility data (i.e.
+taxicab pick-ups and drop-offs).
+In our system, the semantics of labels are expressed through urban activities and urban features, both of which are extracted from textual data (i.e.
+online review data).
+On the other hand, the identification of functional region is based on mobility patterns.
+To generate reasonable explanations, our system blends in the semantics extracted from textual data and moving patterns discovered in mobility data.
+
 In building such a system, we face two challenges.
@@
 %manual label costly supervision in sufficient
-The first one of it is to extract the urban feature from comment data.
-Urban feature is a set of characters with special geographical attributes, e.g., clothes, school, bars and so on.
-Most of our content data are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
-Therefore, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
-In order to get the location information from these content data, all features are extracted as~\cite{Zhang2015Sentires}.
-We select typical features with a high frequency and high information entropy from it.
+The first challenge is how to efficiently extract urban features from online review data.
+A naive approach is to maintain a manually constructed lexicon of urban features.
+However, the lexicon is expensive to construct and maintain.
+An alternative approach is to classify textual phrases with the supervision of a labelled set.
+Again, the supervision is costly to obtain.
 
 %unsupervised
+To address the first challenge, we adopt an unsupervised approach to extract urban features from online review data.
+Furthermore, urban features are characterized with geographical attributes, existing product feature extraction methods such as~\cite{Lu2011Label} are not directly applicable.
+We implement a layered computation.
+We first adopt NLP techniques to select a candidate set of features.  
+Then we filter urban features which are most representative in geographical texts.
 
 %how to embed mobility data
-And the second challenge is how to explain the features.
-If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not have a strong explanation power for the identification, or even will not be generated.
-To improve the explanation power of our framework, we extract related urban feature and find the corresponding sentiment score between activity and urban feature from contents.
-With the probability that region units belong to which function generated by DMR, we can applied matrix factorization to find the relativity between region units and latent factor, i,e urban feature.
-The urban feature with highest relativity make an explanation for why corresponding region units are identified as such function.
+The second challenge arises from the integration of textual and mobility data.
+To fully explain the functional of a region, our goal is to simultaneously discover semantic associations (i.e.
+how the given region is associated to each urban activity and urban feature) and mobility patterns (i.e.
+how the current traffic flow of a given region is affected by previous traffic flow).
+This is not a trivial task.
+The mobility patterns can be highly diverse for each region and each timepoint.
+For example, people tend to gather in school region in the day, while in residence regions produces maximal traffic flow at night.
+Restraining a global form shared by all mobility patterns is problematic.
+
+To address the second challenge, we adopt a latent factor model to embed the semantic associations to predict traffic flows, i.e.
+the traffic flow of a region is aggregated over all activities, where each activity specific traffic flow is predicted by people's preferences on multiple urban features and the region's association with the same set of urban features.
+Furthermore, we incorporate a bias curve in the prediction formula to represent mobility patterns. 
+The bias curve is free shaped so that the forms of mobility patterns are not restrained
 
@@
 
-\textbf{Contribution.}
-Our paper has an outstanding result in following several aspect:
+\textbf{Contribution} of this work is three-fold:
 \begin{itemize}

### 2018-11-23 paper.tex
related

@@
 \begin{document}
-\title{Explain urban regional function}
+\title{Explainable Functional Region Identification}
 \author{Submission}
@@
 %motivation
-There is a strong incentive to develop explainable FRI system, which \emph{explains} the identification of functional regions. 
-Explainable FRI is beneficial for both system designers and end users.
+There is a strong incentive to develop  \emph{Explainable Functional Region Identification} (EFRI) system, which \emph{explains} the identification of functional regions. 
+EFRI is beneficial for both system designers and end users.
 For system designers, explanations help them better diagnose the system and improve system performance. 
@@
 Though there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
-In this paper, we present a novel system for explainable FRI by integrating heterogeneous data sources.
+In this paper, we present a novel EFRI system by integrating heterogeneous data sources.
 Our system provides post-hoc explanations, i.e.
@@
 %highlight
-We highlight a key property of the proposed explainable FRI system: \textbf{the power to integrate heterogenous data sources to offer semantic explanations for mobility patterns}.
+We highlight a key property of the proposed EFRI system: \textbf{the power to integrate heterogenous data sources to offer semantic explanations for mobility patterns}.
 On one hand, explanations essentially involve semantics, which are not available in pure mobility data (i.e.
@@
 To address the first challenge, we adopt an unsupervised approach to extract urban features from online review data.
-Furthermore, urban features are characterized with geographical attributes, existing product feature extraction methods such as~\cite{Lu2011Label} are not directly applicable.
-We implement a layered computation.
-We first adopt NLP techniques to select a candidate set of features.  
+Urban features are characterized with geographical attributes, existing product feature extraction methods such as~\cite{Lu2011Label} are not directly applicable.
+Therefore, we first adopt NLP techniques to select a candidate set of features.  
 Then we filter urban features which are most representative in geographical texts.
@@
 This is not a trivial task.
-The mobility patterns can be highly diverse for each region and each timepoint.
-For example, people tend to gather in school region in the day, while in residence regions produces maximal traffic flow at night.
+The mobility patterns can be highly diverse for each region and time sensitive.
+For example, people tend to gather in school region in the day, while in residence regions produces they gather at night.
 Restraining a global form shared by all mobility patterns is problematic.
 
-To address the second challenge, we adopt a latent factor model to embed the semantic associations to predict traffic flows, i.e.
+%bias curve
+To address the second challenge, we adopt a layered regression model to embed the semantic associations to predict traffic flows, i.e.
 the traffic flow of a region is aggregated over all activities, where each activity specific traffic flow is predicted by people's preferences on multiple urban features and the region's association with the same set of urban features.
 Furthermore, we incorporate a bias curve in the prediction formula to represent mobility patterns. 
-The bias curve is free shaped so that the forms of mobility patterns are not restrained
+The bias curve is free shaped so that the forms of mobility patterns are not restrained.
 
-%bias curve
-
-\textbf{Contribution} of this work is three-fold:
-\begin{itemize}
-  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of users and urban system designers.
-  \item After identify different functions, We use the contents with sentiment to find the typical urban feature within a region and make explanation.
-  \item The explanation is given by latent factor model. We appplied matrix factorization to get the correlation coefficients between single region units and its features.
-\end{itemize}
+%contribution
+Contribution of this work is three-fold.
+(1) \textbf{An Unexplored Problem.} To the best of our knowledge, we are the first to study the problem of explainable functional region identification.
+(2) \textbf{A New Form of Explanations.} We propose a novel framework to deliver explanations.
+The proposed EFRI explains the functional of a region by demonstrating both the semantics of functional (through urban activities and urban features) and mobility patterns of the functional (time sensitive mobility patterns).
+Such informative explanations can greatly improve user experience and might shed some insights in other domains such as explainable recommendations.
+(3) \textbf{A Novel Model.} We present a unsupervised framework to extract urban activities and urban features from online review data.
+We then adopt a layered regression model to semanticaly associate regions to urban features.
+We also embed a free-form bias curve to represent mobility pattrerns in mobility data.
 
 The remainder of the paper is organized as follows.
-We give an overview for related work in Section 2.
-In Section 3, we give an overview of our framework.
-Section 4 shows the process of functional region identification as well as urban feature extraction.
-And Section 5 introduces the post hoc explanation model.
-We test the framework on our datasets and presents the superior explanation result in Section 6
-Finally, we made a conclusion and looked forward to our future work in Section 7.
+We briefly overview related work in Section~\ref{sec:related}.
+The EFRI system is presented in Section~\ref{sec:extraction} and Section~\ref{sec:regression}. 
+In Section~\ref{sec:extraction}, we describe technical details to extract urban activities and urban features in online review data.
+In Section~\ref{sec:regression}, we give the intuition and inference of the layered regression model to generate explanations that cover both semantic associations and mobility patterns.
+We evaluate the EFRI system and analyze the experimental results in Section~\ref{sec:experiments}.
+Finally, we conclude this work in Section~\ref{sec:conclusions}.
 
-\section{Related Work}
-Our work is build upon taxicabs trajectory and comment text.
-With the data source, two lines of work are related to this paper: urban computing and online sentiment analysis .
+\section{Related Work}\label{sec:related}
+As our work makes use of taxicab pick-ups and drop-offs data and online review data, two lines of work are related: urban computing on mobility data and online review analysis .
 
 %related work section name, find another suitable name for mobility mining
-\subsection{Urban Computing}
+\subsection{Urban Computing on Mobility Data}
+%data source
+Urban computing~\cite{Zheng2014UrbanConcepts} tackles issues that cities face by analyzing human mobility data.
+Major sources of mobility data are check-ins data~\cite{Cheng2011Check-in,Gallegos16happier}, origin-destination pairs data~\cite{Ge2011TaxiBusiness,Meng2017Traffic}  and trajectory data~\cite{Ge2011TaxiBusiness,Garg2018Route,Wu2017Reachable,Wang2018Deep}.The simplest form among them are check-ins data, which is a set of points revealing users' current locations collected from location sharing services.
+Check-ins data are previously adopted for revealing demographic associations~\cite{Gallegos16happier} and POI recommendation~\cite{Cheng2011Check-in}.
+Origin-destination data consists of a set of pairwise location points, e.g.
+a pick-up point and a drop-off point of a taxi trajectory.
+Most functional region identification systems are based on origin-destination pairs~\cite{,Karlsson2006FunctionalRegionSummary}, e.g.
+from commute data~\cite{Farmer2009Overvie, Korpan2017navigation,Jose2018cognitive}, or from remote-sensor image data~\cite{Vatsavai2011Remote}.
+Trajectory data consists of a set of routes, where each route is a sequence of location points.
+Taxi driver trajectory~\cite{Ge2011TaxiBusiness,Garg2018Route} data is more suitable for traffic planning.
 
-Urban computing~\cite{Zheng2014UrbanConcepts} tackles the major issues that cities face by analyzing human mobility collected from different sensors.
-Major sources of human mobility data are check-ins in POI~\cite{Gallegos16happier}, pick-up and drop-off behavior of taxicabs~\cite{Ge2011TaxiBusiness,Meng2017Traffic} in different locations and  trajectories.
+%functional region identification
+A major and ongoing thrust of research on urban computing concerns the identification of functional regions.
+In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
+Recent studies focus on city-level FRI, i.e.
+identification of regions in a city that support certain needs of urban lives ~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+Traditional FRI systems are rule-based~\cite{Ball1980Definition}, i.e.
+a city's labor market statistics satisfying certain requirements is considered to be a functional region.
+Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
+Most of them use clustering methods~\cite{Karlsson2006FunctionalRegionSummary}.
+To name a few, clustering algorithm based on the 'modularity function'~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering~\cite{Vatsavai2011Remote}, Latent Dirichlet Allocation (LDA)~\cite{Vatsavai2010Remote} and Dirichlet Multinomial Regression (DMR)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
 
-%extract the different among these data
-The simplest form of mobility data is \textbf{check-ins data}, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
-Statistical association analysis is commonly conducted on check-ins.
-For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
-A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers refueling decision~\cite{Zhang2015Fuel}.
+%drawbacks
+Existing urban computing systems extensively rely on complex machine learning algorithms hence they act as blank-boxes for end users.
+The lack of explanation weakens the persuasiveness and trustworthiness of the system for end-users.
+Our work is to make up for this drawback by providing intuitive explanations of the results for end-users and system designers
 
-The second form of mobility data is \textbf{origin-destination pairs}, i.e. a pick-up point and a drop-off point of a taxi trajectory.
-Clustering methods including Newman modularity cluster algorithm~\cite{Newman2004ModularityFunction} are applied in functional region identification~\cite{Ratti2010Telecom}.
-Recently, latent factor models are proposed to treat a region as document and infer functional-specific ~\cite{Yuan2012FunctionRegion}.%
-Latent activity is imported in topic model in~\cite{Yuan2015FunctionRegion} to define the specific functions of different regions.
-
-Alternatives for origin-destination pairs are \textbf{trajectory data}.
-Applications on trajectory data include recommendation, e.g.
-to recommend more suitable place to drivers~\cite{Ge2011TaxiBusiness,Garg2018Route} and traffic planning, e.g.
-to find reachable region within a given temporal period~\cite{Wu2017Reachable}, %find a fast route
-or to predict travel time~\cite{Wang2018Deep}.
-
-In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
-Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
-Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
-Later work focuses on city-level functional region identification,
-
-%tasks
-However, existing urban computing systems extensively rely on complex machine learning algorithms hence they act as blank-boxes for end users.
-The lack of explanation weakens the persuasiveness and trustworthiness of the system for users.
-Our work is to make up for this drawback by providing intuitive explanations of the results for users or system designers
-
-\subsection{Geographical Analysis of Online Sentiment}
+\subsection{Online Review Analysis}
+Online review data has been extensively studied in opinion mining~\cite{}.
+Given a set of product features, the user sentiments in each review are extracted either as binary sentiment polarity~\cite{} or as numerical sentimental strength~\cite{}.
+Opinion mining has been combined with recommender systems to generate explainable recommendations~\cite{}.
+Typically, a latent factor model~\cite{} is utilized to decompose user-item ratings to a latent feature space of user preferences and item attributes.
+Though there are fruitful research results in this domain, due to the lack of geographical analysis, these methods are not directly applicable to generate explanations for FRI.
 
@@
 
-%and emotion
-%complete survey
 However, most existing work of this line employ simple statistical analysis to uncover the associations.
@@
 
-\section{Urban Feature}
-\subsection{Functional Region Identification}
-A city was segmented into single region units, which is regarded as documents with various themes in topic modeling.
-DMR~\cite{Mimno2012DMR} was applied in functional region identification as explained in~\cite{Yuan2012FunctionRegion}.
-DMR, whose structure is illustrated in Figure~\ref{DMR_ori}, is a topic clustering model based on Latent Dirichlet Allocation(LDA).
-It input some metadata, e.g. authors and publishers, in addtion to basic LDA, which make the topic modeling more accurate.
-As describe in~\cite{Yuan2012FunctionRegion},we regard flow increment calculated in regions as vocabulary in documents, which is marked as $m_{r,n}$ in Figure~\ref{DMR_ori}.
-And POI located in different region units are correlate to the matadata of document, which is marked as $x_r$ in Figure~\ref{DMR_ori}.
-\begin{figure}[h]
-  \centering
-  \includegraphics[scale=0.4]{DMR.png}
-  \caption{The structure of DMR}
-  \label{DMR_ori}
-\end{figure}
+\section{Urban Feature}\label{sec:extraction}
 
@@
 
-\section{Explanation Model}
+\section{Explanation Model}\label{sec:regression}
 In this section,we describe our post hoc framework for explanation in detail.
@@
 
-\section{Experiments}
+\section{Experiments}\label{sec:experiments}
 \subsection{Data Set}
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusions}
 Function regions identification is an important part of urban computing.

### 2018-11-24 paper.tex
model

@@
 %motivation
-There is a strong incentive to develop  \emph{Explainable Functional Region Identification} (EFRI) system, which \emph{explains} the identification of functional regions. 
+With the massive amount of geo-tagged textual data online, such as reviews on Points of Interest (POIs), it is possible to develop  \emph{Explainable Functional Region Identification} (EFRI) system, which \emph{explains} the identification of functional regions.
 EFRI is beneficial for both system designers and end users.
@@
 the explanations are not relevant to the FRI algorithm.
-Instead, for an arbitrary FRI algorithm, the system attempts to resolve the ``semantics" of the generated cluster labels by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features for each activity; and (3) listing the most important urban features in the region.
+Instead, for an arbitrary FRI algorithm, the system attempts to resolve the ``semantics" of the generated cluster labels by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features for each activity; and (3) listing the most relevant urban features in the region.
 
@@
 As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions.
-For a specific region $r_1$ with label $l$, the system delivers textual and visual descriptions.
-Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from the analysis of mobility data, these two activities bring in $\%$ of the traffic flow to region $r_1$.
+For a specific region $r$ with label $l$, the system delivers textual and visual descriptions.
+Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from mobility data, coefficients of activity ``'' and ``'' to the traffic flow of region $r$ are $0.6$ and $0.4$ respectively.
 Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews.
-Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system explains why $r_1$ is labeled as $l$.
+Finally region $r$'s most representative urban features are exactly ``" and ``", thus the system explains why $r$ is labeled as $l$.
 
@@
 In our system, the semantics of labels are expressed through urban activities and urban features, both of which are extracted from textual data (i.e.
-online review data).
+online POI review data).
 On the other hand, the identification of functional region is based on mobility patterns.
-To generate reasonable explanations, our system blends in the semantics extracted from textual data and moving patterns discovered in mobility data.
+To generate reasonable explanations, our system blends the semantics extracted from textual data with moving patterns discovered in mobility data.
 
@@
 \centering
-\subfigure[An example of our identification result]{
-\label{real-map} %% label for first subfigure
-\includegraphics[width=1.5in]{example-net.png}}
-\subfigure[moving patterns]{
-\label{patterns} %% label for second subfigure
-\includegraphics[width=1.4in]{example-line.png}}
-\subfigure[POIs in different functional region]{
-\label{sentiment} %% label for second subfigure
-\includegraphics[width=1.4in]{example-sentiment.png}}
-\caption{The explanation provided for functional region identification.
-Region I in Fig.\ref{real-map} is labeled as residential region while II is commercial region.
-Fig.\ref{patterns} revealed differences of the mobility patterns between residential region and commercial region,workdays and weekends.
-Fig.\ref{POI} shows the distribution of POIs within the two regions,e.g. there is more shops in commercial region.
-And from fig.\ref{sentiment} we find that people have a more interest in a positive sentiment in traffic for commercial and pay more attention to noise for residential region.}
+\caption{An illustrative example of Explainable Functional Region Identification (EFRI)}
 \label{explanation-example} %% label for entire figure
@@
 This is not a trivial task.
-The mobility patterns can be highly diverse for each region and time sensitive.
+The mobility patterns can be highly diverse for each activity and time sensitive.
 For example, people tend to gather in school region in the day, while in residence regions produces they gather at night.
@@
 
-\section{System Overview}
-The section make an overview introduction for our post hoc framework to explain the functional region identification.
-The whole structure is illustrated in Figure ~\ref{overview} while the corresponding steps as follow:
+\section{Urban Opinion Extraction}\label{sec:extraction}
+%system overview
+As shown in Fig.~\ref{explanation-example}, to generate the explanations, the proposed EFRI system consists of two components: (1) \textbf{Urban Opinion Extraction} module works with textual data, such as online POI review data.
+To be specific, this module first extracts a set of textual phrases that represent urban activities and group the online review data based on activities, then it extracts a set of urban features in each review, finally it extracts the public sentiments on each urban feature under each activity.
+(2)\textbf{Layered Regression} module works with the results from \textbf{Urban Opinion Extraction} module and mobility data, such as taxicab pick-up and drop-offs data.
+This module will be discussed in later sections.
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[scale=0.3]{overview.png}
-  \label{overview}
-  \caption{The overview structure of our framework}
-\end{figure}
+\subsection{Urban Activity Extraction}
+%technical details for extracting textual phrases 
+To obtain a high-quality seed list of phrases , we start with a taxonomy of urban activities. Describe the taxonomy here, number of activities, why it is good to start with, etc.
 
-\emph{1.Functional region identification:}
+%is it too many or too few? If it's too many, use the seed list as a supervision set. If it's too few, describe the filtering method below.
+However, the seed list is too ...
+Intuitively, a good activity phrase should...
+Therefore, ...
 
-The input data of first step is taxicabs OD pairs and POIs with coordinates.
-We can get an activity-region matrix with value of the probability that each single region units belong to each activity by DMR.
-And for the region, an activity with highest probability can be output as the function of this region.
-
-\emph{2.Urban feature extraction:}
-
-This step based upon the comments of different shops and activity-region matrix output in last step.
-We select nouns with high frequency and low information entropy as our urban features.
-Meanwhile, the sentiment analyse between urban feature and different activity is also illustrated in an activity-feature matrix.
-
-\emph{3.Train Matrix Factorization model:}
-
-With the certain activity-region matrix $\bm{r}$ and activity-feature matrix $\bm{u}$, we performed an matrix factorization model in form of Equation \ref{model} to get the region-feature matrix $\bm{v}$.
-Training data comes from the given result of step 1 and step 2.
-
-\emph{4.Output label explanation:}
-
-The region-feature matrix $\bm{v}$ generated in step 3 in the input of this step
-For each single region units,we can pick the urban features with highest sentiment score in $\bm{v}$.
-These urban feature is the explanation for the functional region identification.
-
-\section{Urban Feature}\label{sec:extraction}
+%group textual data based on activity
+We obtain a set of activity phrases $\mathcal{A}=\{a\}$ after the above two steps.
+We group the textual data based on the recognized activity phrases. 
+Technical details here...specify what you do when there are several activities in a sentence/review.
 
 \subsection{Urban Feature Extraction}
-To get proper urban features for explaining different functions, we thought that urban features should be nouns with high frequency and low information entropy.
+%features
+Previous studies on opinion mining for product recommendations~\cite{} have achieved remarkable success in extracting product aspects, i.e. with a precision as high as $\%$.
+Inspired by~\cite{}, we also use a rule-based approach to extract a candidate list for urban features.
+As we are building a candidate list, the primal objective is to obtain high coverage instead of high precision. 
+We modify the rules to (if necessary, add a table of rules here)...
+Technical details here...
 
-Considering the property of urban features, we separate comment sentences into single words and select all nouns of it.
-With the help of coordinates, these words can correspond to different single units.
-Take the sparseness of latent factor into account, we thought the words had better appear in more region units.
-And we filer the high-frequency nouns as features.
-If the frequency of a word is high enough, i.e. the shops commented with this word is much than a threshold $t$, we thought its frequency is high.
-We set the threshold $t$ as 500.
+%filter features
+\emph{Urban features} distinguish with product aspect in that ...
+Intuitively, a phrase indicating an urban feature must...
+As forth, we use statistics such as ...
 
-Meanwhile, to make the urban features more distinguishing, we calculate the information entropy of words for different functional regions generated in Section 4.1.
-Information entropy can measure the amount of information that a word contains.
-Stronger distinguishing ability of a word takes lower information entropy.
-The information entropy is defined as:
-$$H[x_i,word_j] = -\sum_i p(x_i,word_j)\log p(x_i,word_j)$$
-where $x_i$ stands for $i$th functional regions;
-$p(x_i,word_j)$ is the proportion of shops located in $i$th functional regions commented with $j$th word in all shops located in $i$th functional regions.
-We select features with lowest information entropy as our urban features, which are shown in Table \ref{urbanfeatures}.
+Equation here
+
+As shown in Table~\ref{tab:urbanfeatures}
 
@@
 \caption{Selected Urban Features}
-\label{urbanfeatures}
+\label{tab:urbanfeatures}
 \begin{tabular}{c|c|c|c|c}
@@
 
-\subsection{Urban Feature Matrix}
+\subsection{Urban Sentiment Extraction}
+%sentiment 
+We do not focus on word-level sentiment analysis in this paper.
+The state-of-the-art toolkit is used...
+technical details here
 
-\section{Explanation Model}\label{sec:regression}
-In this section,we describe our post hoc framework for explanation in detail.
+%aggregate sentiments
+However, the problem of aggregating word-level sentiments to activity must be addressed.
+intuition here...
+technical details here...
+result is $U_a$, describe
 
-\subsection{Latent Factor Model}
-A classical model has Intuitive explanation is latent factor model.
-It has a wide application in various fields.
-The form of latent factor applied in recommendation system to predict rating of user $u$ to product $p$ as follow:
+\section{Layered Regression Model}\label{sec:regression}
+%preliminaries
+In this section, we describe in detail the layered regression model.
+Hereafter, unless stated otherwise, we use lower-case letters for indices, uppercase letters for sets, lower-case bold-face letters for vectors and upper-case bold-face letters for matrices.
+To be specific, an arbitrary FRI system divides a city into a set of regions, denoted as $r\in R$ and each region $r$ is labeled by $l\in L$.
+From textual data, the urban opinion extraction module obtains public sentiment $\mathbf{U}_a\in \mathcal{R}^{K}$ on each activity $a\in A$, where $\mathbf{U}_{a,k}$ is the public sentiment on urban feature $k$ under activity $a$.
+The mobility data consists of number of visitors $f_{r,t}$ for each region $r\in R$ at each time-point $t=1,\cdots,T$.
+$f_{r,t}$ can only be non-negative.
+More notations are shown in Table~\ref{tab:notation}
+
+\begin{table}[htp]
+\caption{Notations for layered regression model}
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+Notation & Description \\\hline
+${A}=\{a\}$ & a set of activities \\
+${R}=\{r\}$ & a set of regions \\
+${L}=\{l\}$ & a set of labels \\
+$F=\{f_{r,l,t}|f_{r,l,t}\geq 0\}$ & A set of observed number of visitors for region $r$ with label $l$ at time $t$ \\
+$\mathbf{U}_a\in \mathcal{R}^K$ & Extracted public sentiments on each urban feature under activity $a$ \\
+$\mathbf{V}_r\in \mathcal{R}^K$ & Parameter representing the relevance of each urban feature to region $r$\\
+$\mathbf{c}_{l}\in \mathcal{R}^{|A|}$ & Coefficient of label $l$ to each activity\\
+$b_t$ &  Traffic flow bias at time $t$\\ 
+\hline
+\end{tabular}
+\end{center}
+\label{tab:notation}
+\end{table}%
+
+\subsection{Traffic Flow Prediction}
+Our model builds on a simple intuition, that the more people will visit a region $r$ to perform an activity $a$, if the region $r$ is more relevant to the desired urban features under the activity $a$.
+The desired urban features under activity $a$ is encoded in $\mathbf{U}_a$ which is extracted from online review data.
+The relevance of region $r$ to each urban feature is encoded in $\mathbf{V}_r$ which needs to be learnt. 
+Therefore, the number of visitors $\hat{f}_{r,a}$ can be predicted as follows:
+\begin{equation}\label{equ:fra}
+\hat{f}_{r,a}= \mathbf{U}_a^T \mathbf{V}_r
+\end{equation}
+
+Clearly, people visit a place to perform various activities.
+Thus for a region $r$ at time $t$, the traffic flow is aggregated over all possible activities. This leads to the following equation:
 \begin{equation}
-\hat{r}_{u,p}= g+b_u+b_p+\bm{x_u}^T\bm{y_p} \label{basic}
+\hat{f}_{r,l,t}=b_t+\sum_{a} \mathbf{c}_{l,a} \mathbf{U}_a^T V_r+ \sum_a \beta_{a,t} (f_{r,l,t-1})\label{equ:model}
 \end{equation}
-where $g$ is a base rating in the system while $b_u$ and $b_p$ is the bias of user $u$ and product $p$;
-$\bm{x_u}$ and $\bm{y_p}$ denote vectors of latent factors for corresponding user and product.
+where in the left $\hat{f}_{r,l,t}$ is the observed traffic flow at time $t$ for region $r$ that has been labeled $l$ in the mobility data.
+In the right, the first term $b_t$ is a bias term, the second term considers how much traffic flow each activity brings to a region $r$ with label $l$, $\mathbf{c}_{l,a}$ measures coefficients between label $l$ and activity $a$.
+$\mathbf{c}_{l}>\mathbf{0}$.
+It is worthy to note here that $\mathbf{c}_l$ must be learnt across all regions associated with label $l$.
+In this manner, the semantics of label $l$ by the FRI can be interpreted through the activities (the name ``layered'' regression comes from the layered framework of activity and label).
 
-The matrix $r$ is rating that user $u$ give to product $p$.
-Correlate users as activities, products as locations, we translated the matrix into the sentiment analysis score that actitivy $a$ to region $l$.
-We can make our matrix based upon this stand latent factor model presented in Equation \ref{basic}.
+We usually observe mobility patterns for traffic flows.
+These patterns can be highly diverse across activities. 
+For example, school regions (high traffic flow in the day) and business regions (high traffic flow at night) have different mobility patterns.
+Also it is reasonable to assume temporal dependency in traffic flows.
+Again the temporal dependencies vary among activities.
+For example, current number of visitors in business regions might be strongly influenced by previous numbers of visitors, while in school regions the influence is not significant.
 
-\subsection{Our model}
-Considering the temporal attribute of datesets, ~\cite{Zhang2017Model} has proposed an Historical Influence Aware Latent Factor(HIALF) model take the historical influence into account, which fit our intuition well and make the power of explanation stronger.
+Such diverse and dynamic mobility patterns are modeled by the bias curve $\beta_{a,t}(f_{r,l,t-1})$.
+The subscript $a$ suggests that the bias curve is activity specific.
+The subscript $t$ suggests that the bias curve is time sensitive, i.e.
+with different forms at night and in the day.
+To reduce the number of model parameters, we can group $t$ to a limited set of time segments.
+For example, if we consider only ``weekends'', ``weekday day''  and ``weekday night" then there are in total $3\times |A|$ bias curves.
 
-Therefore, we define our matrix factorization model as:
-\begin{equation}
-\hat{r}_{l,i,a}=b_l+U_a^TV_l+\beta(e_{a,i})\label{model}
+To capture the diverse nature of bias curve, the form of $\beta(x)$ is unknown.
+We apply a data-driven approach: kernel regression, which is a typical non-parameter learning method to fit $\beta(x)$.
+
+\begin{equation}\label{eqn:kernel}
+\beta_{a,t} (x) = \frac{\sum_{i=1}^n k_h(x-x_i) y_i}{ \sum_{j=1}^n k_h(x-x_j)}
 \end{equation}
-where $\hat{r}_{l,i,a}$ stands for the predicted probability at $i$-th time bin that region $l$ belongs to activity $a$;
-$b_l$ is the bias of region $l$;
-$\bm{U_a}$ and $\bm{V_l}$ represent the latent feature of activity $a$ and region $l$;
-$e_{a,i}$ generated by prior expectation;
-and $\beta(\cdot)$ demonstrates the bias curve changing with $e_{a,i}$.
-Now we describe how to learn the $\beta(x)$ and generate a more realistic prior expectaion $e_{a,i}$.
 
-\textbf{Modeling the bias curve $\beta(x)$}
-The form of $\beta(x)$ is unknown.
-We can constrain it with a data-driven approach.
-Kernel regression is a kind of typical non-parameter learning and fit the $\beta(x)$ model well.
-
-If we have a set of independent variables $e_l$ and dependent variables $v_l$, and $v_l=\beta(e_l)+\epsilon_l$ where $\epsilon_l$ is the noise from the standard normal distribution, we can defind $\beta(x)$ as:
-$$\beta(x) = \frac{\sum_{k=1}^{n}w(x,e_l)v_l}{\sum_{k=1}^{n}w(x,e_l)}$$
-where $w(x, x_i) = \exp(-\kappa(x-x_i)^2)$ and $\kappa$ is given by 10.
-Actually, $e_l$ is given while $v_l$ is unknown.
-Therefore, we set $e_l$ as several arithmetic progression within data range and $v_l$ is the corresponding unknown parameters so that we can learn them from datasets.
-
-\textbf{Modeling the prior expectation $e_{a,i}$}
-$$e_{a,i} = \frac{\sum_{k=1}^{i-1}\xi(i-k) r_{a,k}}{\sum_{k=1}^{i-1}\xi(i-k)}$$
-where $\xi(d)=\exp(-\gamma\times d)$ is an exponential triggering kernel that models the decrease of histroy influence;
-$\gamma$ controls the degree that history probability influence current probability;
-and $r_{a,k}$ denotes the sentiment of activity $a$ when time bin $k$.
+To obtain the set of samples $\{(x_i,y_i)\},i=1,\cdots,n$, we let $x_i$ to be uniformly sampled from the range of $f_{r,l,t-1}$.
+$k_h(x-x_i)= \exp(-h (x-x_i)^2)$, where $h$ is a hyper-parameter to control the smoothness of the function.
+The set of $y_i$ are to be learnt from data.
 
 \subsection{Model Inference}
-After build a matrix factorization model, we set up objective function as follow:
-\begin{equation}
-F=\sum\limits_{(p,l,u)\in\mathcal{M}}(r_{l,i,a}-\hat{r}_{l,i,a})^2+\lambda_1(b_l^2+||{\bm{y_r}}||_2^2)+\lambda_2(\sum\limits_{l}v_l^2)+\lambda_3(\sum\limits_{\alpha}\alpha_u^2)
-\label{inference}
-\end{equation}
-where $\Theta$ stands for the unknown parameters, $\bm{y_p}$, $b_u$, $\alpha$ and $v_l$.
-$\mathcal{M}$ contains all $(p,l,u)$ pairs, and each pair of it stands for the related parameter of region $l$ belongs to activity $a$ at time bin $i$.
-$r_{r,i,a}$ is the probability generated by DMR while $\hat{r}_{r,i,a}$ is the predicted probability by Equation \ref{model}.
-The first item of Equation \ref{inference} is quadratic sums of the difference between real probability $r_{r,i,a}$ and predected probability $\hat{r}_{r,i,a}$.
-To prevent from overfitting, we three regularization terms and $\lambda_1$, $\lambda_2$ and $\lambda_3$ are given as hyperparameters.
+Finally, we set up the objective function for layered regression model.
+\begin{eqnarray}
+\min \mathcal{L} & =\sum_{f_{r,l,t}\in F}(f_{r,l,t}-\hat{r}_{r,l,t})^2+\lambda_1 (\sum_t b_t^2  + \sum_r \|\mathbf{V}_r\|^2 )\\\nonumber
+& +\lambda_2(\sum_l \|\mathbf{c}_l\|_1)+\lambda_3(\sum_i y_i^2)\\\nonumber
+& w.r.t. \forall l, \mathbf{c}_l\geq \mathbf{0}
+\label{equ:loss}
+\end{eqnarray}
 
-To get our optimal $\bm{y_r}$, we aim to solve the following optimization problem and make the predicted probability $\hat{r}_{r,i,a}$ as close as possible to the real probability$r_{r,i,a}$:
-$$\min\limits_{\Theta} F$$
-The approach to get it is stochastic gradient descent(SGD) algorithm due to its efficiency in learning the parameter of objective function
+The first term in Equ.~\ref{equ:loss} minimizes the differences between observed traffic flow and predicted traffic flow by Equ.~\ref{equ:model}.
+The second term avoids over-fitting by adding a L2 penalty term on model parameters $b_t, \mathbf{V}_r$.
+The third term further regularizes the squared loss by adopting a L1 term on $\mathbf{c}_l$.
+The sparseness constraint on $\mathbf{c}_l$ helps to represent a label by the most representative activity.
+
+The parameters are inferred by stochastic gradient.
+
+\begin{eqnarray}
+inference equation here
+\label{equ:sgd}
+\end{eqnarray}
 
@@
 
-\bibitem{Zhang2018SIGIR}Yongfeng Zhang, Yi Zhang, and Min Zhang.
-SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018).
-In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 18).
-2018.
-
 \bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. arXiv preprint arXiv:1804.11192. 2018.

### 2018-11-24 paper.tex
beta
experiment framework

@@
 \begin{equation}
-\hat{f}_{r,l,t}=b_t+\sum_{a} \mathbf{c}_{l,a} \mathbf{U}_a^T V_r+ \sum_a \beta_{a,t} (f_{r,l,t-1})\label{equ:model}
+\hat{f}_{r,l,t}=b_t+\sum_{a} \mathbf{c}_{l,a} [\mathbf{U}_a^T V_r+  \beta_{a,t} (f_{r,l,t-1})] \label{equ:model}
 \end{equation}
@@
 \section{Experiments}\label{sec:experiments}
-\subsection{Data Set}
-The data set for our experiments including both mobility data and content data.
-The mobility data including the pick-up and drop-off timestamps and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
-And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping, which helps sentiment analysis of the regions.
-\begin{table}[h]
-\caption{Statistics of datasets}\label{dataset}
-\begin{tabular}{|l|l|c|}
-\hline
-Datasets &  attributes & Value\\
-\hline
-comments & shops with coordinates(POI) & 109686\\
- & shops with comments & 50853\\
- & total comments & 3213264\\
-\hline
-taxicabs & effective orders & 7065937\\
- & effective days & 30 \\
-\hline
-road networks & geographical scope & [103.93$^\circ$E,104.21$^\circ$E] and [30.56$^\circ$N,30.79$^\circ$N]\\
- & road segments & 3712\\
- & percentage of major roads & 54.9\%\\
- & segmented regions & 901\\
-\hline
-\end{tabular}
-\end{table}
+In this section we ask the following research questions. 
+(1) Does the proposed EFRI framework accurately extract urban features?  
+(2) Does EFRI capture the mobility patterns?
+(3) Does EFRI improve the interpretability of FRI results?
 
-\subsection{Preparation}
-To form the basic region of city,we segment the urban area of city into region units by the major road network and make a map simplification.
-The longitude of map range is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.
-Raster-based model is more computationally efficient and succinct for territorial analysis, which is suitable for our map scenario.
-We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid.
-In the grid, the road network is converted to a binary image, as 1 stands for the road while 0 stands for the blank areas.
+\subsection{Experimental Setup}
+The data sets for our experiments include a mobility data set and a textual data set.
+The mobility data (Didi dataset) is a set of  pick-up and drop-off coordinates of taxicabs with timestamps.
+Statistics: e.g. number of pickup-dropoffs , time period, in which city....
+The textual data set (Dianping dataset) is a set of ...
+It is crawled from China's largest online review sits\footnote{www.dianping.com.cn} in ....
+The data set contains xxx POIs, xxx comments
 
-The main road data is present in Fig.\ref{raw_map}, including motorway, trunk, primary, secondary, tertiary and their links.
-But the Fig.\ref{raw_map} is full of some unnecessary details, such as the lanes of a road and the overpasses, which disturb the distribution of regions.
-As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process illustrated in Figure~\ref{dilation and thinning} are operated on the original road data to remove some small regions and simplify the map.
-\begin{figure}[h]
-    \centering
-    \subfigure[Original segment of city]{
-    \label{raw_map} %% label for first subfigure
-    \includegraphics[width=1.5in]{chengdu_1.png}}
-    \subfigure[After dilation operator]{
-    \label{dilation} %% label for second subfigure
-    \includegraphics[width=1.5in]{chengdu_2.png}}
-    \subfigure[After thinning operator]{
-    \label{thinning} %% label for second subfigure
-    \includegraphics[width=1.5in]{chengdu_3.png}}
-    \caption{The preparation process of road network}
-    \label{dilation and thinning} %% label for entire figure
-\end{figure}
+\subsection{Pre-processing}
 
-We use DMR to identify regions into 8/4 types with different regions, which is illustrated in Figure~\ref{DMR_result}
-The main function regions in the city is residence region, business region, study and science region, scenery regions and so on.
+%preprocessing
+To obtain the input for EFRI, we implement four pre-processing steps: (1) region segmentation; (2) FRI on mobility data; (3) data set linking; (4) text cleaning.
+
+\textbf{Region segmentation.} To form the basic city regions, we segment the urban area by the city's major road network.
+The longitude of the map range in Didi dataset is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.% do we have to provide the range?
+in other words, how do you get the range?
+We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid by the Raster-based model~\cite{}.
+The road network is converted to a grey image, where in each grid 1 stands for the road and $0$ otherwise. %?????
+ The dilation and thinning process~\cite{} is operated to remove small regions such as lanes and road overpasses and simplify the map.
+
+\textbf{FRI on mobility data.} We use DMR~\cite{} to identify region functionals and label them with  8/4 types. % what do you mean by 8/4?
+Any parameters in DMR?
+Note that we can use any convenient FRI system to identify region functionals.
+The DMR results are illustrated in Figure~\ref{fig:DMR}
 
@@
 \caption{results of DMR}
-\label{The results of functional region identification}
+\label{fig:DMR}
 \end{figure}
 
-\subsection{Evaluation Metrics}
-We evaluate the functional region through two approaches.
-One is the percentage of regions that could find explanation label by our framework; while the other is the quality and accuracy of the explanation given by our framework.
+\textbf{Data set linking.} we ??how do you link the two datasets?
+remove any POIs?
 
-For the evaluation of percentage of explainable region, we put forward the $explanation percentage$ to measure the proportion that regions with explainable labels as:
+\textbf{Text Cleaning.} Chinese word segmentation? stopword removal?
+activity extraction?
+Statistics of the combined dataset are shown in Table~\ref{tab:dataset}.
+Averagely, a POI is associated with xxx comments....more statistics
+
+\begin{table}[h]
+\caption{Statistics of dataset}\label{tab:dataset}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\#POIs & \#Comments & \#Mobility pairs & \#Regions & \#Labels \\
+\end{tabular}
+\end{table}
+
+\subsection{Urban Feature Extraction}
+
+\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) (2) (3) (4) (5)
+
+\textbf{Evaluation metrics.} (1) (2) (3) (4)equations here
+
+\begin{table}[h]
+\caption{Comparative performance of urban feature extraction}\label{tab:extraction}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Method & Metric 1 & Metric 2 & Metric 3 & Metric 4\\\hline
+\end{tabular}
+\end{table}
+
+As shown in Table~\ref{tab:extraction}, your analysis here.
+
+\subsection{Explainability Performance}
+
+\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) (2) (3)
+
+\textbf{Evaluation metrics.} Evaluation of explainable systems is still an open problem.
+In this work, we consider two categories of evaluation metrics.
+The first is objective to evaluate the quantity of explanations.
+(1) EP: percentage of regions that could find explanation label by our framework.
+The rest are subjective to evaluate the quality of explanations.
+(2) (3) (4) All reported results are averaged over regions.
+
+equations here 
 $$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$
 
-For the second approach,we take a metric to measure the quality and accuracy of our explanation label.
+\textbf{Evaluation Process}  how many human judges? how to vote?
 
-\subsection{Baseline and other comparison}
+\begin{table}[h]
+\caption{Comparative performance of explainability }\label{tab:explainablity}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Method & Metric 1 & Metric 2 & Metric 3 & Metric 4\\\hline
+\end{tabular}
+\end{table}
 
-\subsection{result}
+As shown in Table~\ref{tab:explainability}, your analysis here.
+
+\subsection{Case Study}
+Finally we demonstrate a case study. As shown Figure~\ref{fig:DMR}, regions in the city can be roughly classified as residence region, business region, study and science region and scenery regions.
 \begin{table}[h]

### 2018-11-25 paper.tex
abstractconclusion

@@
 \begin{abstract}
-Functional region identification is a critical step towards Urban computing.
-The state-of-the-art Dirichlet Multinomial Regression(DMR) has identify regions with different function based on topic cluster modeling.
-Due to the ingenious structure inside the complex model, its result is beyond the direct comprehension of humans.
-How to give them reliable explanations are the main objectives of this work.
-To improve the persuasiveness of its result, we proposed a post hoc framework to make explanation for it.
-Optimal latent factor model was applied as explanation after the identification.
-We use matrix factorization to get latent factors and correlate latent factors with urban feature.
-The selected urban feature can be labeled as the explanation.
-Our framework can give an strong evidence to the identification and enhance the satisfaction of users and system designers.
-
-(15--250 words.)
+As a critical step in urban computing, functional region identification (FRI) has attracted a lot of research attention.
+Existing research generally cluster city regions based on human mobility data where the cluster labels are difficult to interpret.
+In this paper, we explore the problem of explainable functional region identification (EFRI), which integrates online geo-tagged textual data and mobility data to deliver explanations of any FRI results.
+We  explain a region's function through a set of urban activities and urban features, which are automatically extracted from online textual data.
+We  build a layered regression model to to infer each region's relevance to urban features.
+The diverse and time-sensitive mobility patterns are encoded in a free-form bias curve in the regression model.
+We conduct comprehensive experiments to verify the accuracy of extracted urban features and the interpretability of the proposed EFRI system.
 
@@
 (3) \textbf{A Novel Model.} We present a unsupervised framework to extract urban activities and urban features from online review data.
-We then adopt a layered regression model to semanticaly associate regions to urban features.
+We then adopt a layered regression model to semantically associate regions to urban features.
 We also embed a free-form bias curve to represent mobility pattrerns in mobility data.
@@
 \section{Conclusion}\label{sec:conclusions}
-Function regions identification is an important part of urban computing.
-But its evaluation depend on human intuition and urban planning, which is hard to display in terms of statistics.
-To make up for the lack of persuasive explanation, we proposed a post hoc framework to give persuasive explanation for functional regions identification in this paper.
-Our datasets including over 3 million comments of shops and taxicabs OD pair trajectory in November 2016 generated by more than 7 million orders.
-We utilized the framework to general most relative labels for every single region units as explanation.
-According to the experiments performed in the datasets, our framework give an strong evidence to the identification and enhance its persuasiveness.
-The result can help users and urban system designers easily recognize the region functions, which is helpful in a variety of urban applications, such as urban planning, location choosing for a business advertisement casting, and so on.
+We present a novel explainable functional region identification (EFRI) system.
+We provide post-hoc explanations which describe the results of any FRI system through a set of urban activities and urban features automatically extracted from online textual data.
+We further embed the diverse and time-sensitive mobility patterns revealed in mobility data with semantic associations in textual data.
+Experiments show that our system can extracted high quality urban features and provide reasonable explanations.
 
-There are some directions can improve in the future work.
-First is to full utilize our data sets of trajectory. 
-Our trajectory datasets not only have origin and destination, but also include the detail points that users have passed by.
-There are also some interesting patterns within these process points, and we can find new moving patterns in it. 
-Second, we want to change our phrase-level explanation into sentence-level, which is more similar to natural language.
+In future work we will explore more information sources such as tweets and news reports to incorporate the power of big data in EFRI.
+With massive amounts of textual data that covers all areas of urban lives, more human activities can be explained.
+Another future direction is to adopt new styles of explanations. 
+For example, explanations in nature language are more friendly to end-users.
+Visualizing the explanations is beneficial for government officers and system designers.
 

### 2018-11-25 paper.tex
补文字部分

@@
 \documentclass[runningheads]{llncs}
+\usepackage{amsmath,amssymb,amstext}
 \usepackage{bm}
@@
 For a specific region $r$ with label $l$, the system delivers textual and visual descriptions.
-Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from mobility data, coefficients of activity ``'' and ``'' to the traffic flow of region $r$ are $0.6$ and $0.4$ respectively.
-Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews.
-Finally region $r$'s most representative urban features are exactly ``" and ``", thus the system explains why $r$ is labeled as $l$.
+Firstly label $l$ is most likely to relate to a mixture of activities ``Business'' and ``School'', because from mobility data, coefficients of activity ``Business'' and ``School'' to the traffic flow of region $r$ are $0.7$ and $0.3$ respectively.
+Secondly, under activity ``Business", two urban features ``Service'' and ``Taste" are most popular, with highly positive sentiments collected from online reviews.
+Finally region $r$'s most representative urban features are exactly ``Service" and ``Taste", thus the system explains why $r$ is labeled as $l$.
 
@@
 \centering
+\includegraphics[scale=0.5]{overview.png}
 \caption{An illustrative example of Explainable Functional Region Identification (EFRI)}
@@
 
-\subsection{Urban Activity Extraction}
+\subsection{Urban Activity Extraction}\label{sec:urbanactivityextraction}
 %technical details for extracting textual phrases
-To obtain a high-quality seed list of phrases , we start with a taxonomy of urban activities. Describe the taxonomy here, number of activities, why it is good to start with, etc.
+To obtain a high-quality seed list of phrases , we start with a taxonomy of urban activities.
+The taxonomy comes from the self-tags that taken by commented items.
+They are given 16 different types of tags, and most of them are consumption.
+They form 16 activity sample in the taxonomy, including Residence, Clothing, Study and Scenery and so on.
+The taxonomy is easy to obtain and can be used for more activities.
 
 %is it too many or too few? If it's too many, use the seed list as a supervision set. If it's too few, describe the filtering method below.
-However, the seed list is too ...
-Intuitively, a good activity phrase should...
-Therefore, ...
+However, the seed list is too few to describe various functions.
+Intuitively, a good activity phrase should have the ability to find the major function of at least a label.
+The quantity of few activity constrains the activities hidden in textual data.
+Therefore, we applied a k-Nearest Neighbor(KNN) to find more activity phrases based on the 16 activity samples mentioned in last step.
+We select all words whose property is noun and sort them into vectors with word embedding.
+By measure the consine distance between two vectors that stands for two words, we can find the k closest neighbors of each word.
+Different with traditional kNN, we aim to find suitable activity features instead of classification.
+A word can be select as activity if the score of positive examples, i.e. selected activity phrases, in its k neighbor are larger than a threshold.
+There is very few positive examples in the beginning, so we give the 16 original activity a large weight.
+Meanwhile, the confidence of later positive examples is set by their neighbors.
+A word with many positive example neighbors and high-weight neighbors would get high weight.
+The process consists until no new activity is found.
 
@@
 We group the textual data based on the recognized activity phrases.
-Technical details here...specify what you do when there are several activities in a sentence/review.
+A sentence include a activity means it is contains relative information about the activity. 
+We can classify it into the responding activity.
+Specially, a sentence may include several activities, which could be analysed in different activities without conflict.
 
-\subsection{Urban Feature Extraction}
+\subsection{Urban Feature Extraction}\label{sec:urbanfeatureextraction}
 %features
-Previous studies on opinion mining for product recommendations~\cite{} have achieved remarkable success in extracting product aspects, i.e. with a precision as high as $\%$.
-Inspired by~\cite{}, we also use a rule-based approach to extract a candidate list for urban features.
+Previous studies on opinion mining for product recommendations~\cite{Zhang2014ExplicitFactor} have achieved remarkable success in extracting product aspects, i.e. with a precision more than $90\%$.
+In our EFRI models, the features would be displayed as explanation for the labels, which relate the activities with labels.
+A high similarity between activities and urban features would help improve the persuasiveness of our explanation.
+In next step, we will find sentiment correlate with urban features in grouped textual data of activity.
+Similarity between activity and features also provide more analytical corpus.
+Therefore, we choose word2vec~\cite{Mikolov2013Word2vec} to find the most relative words between selected activities.
+Word2vec is superior than consine distance in terms of similarity of semantics, for it is based on complex neural network.
+A feature semantically similar to activity make user easier to associate the feature with possible activities.
+Feature is a word with a similarity accumulation with each activity phrase large than a threshold.
+Frequency from statistic is also an important criteria here.
 As we are building a candidate list, the primal objective is to obtain high coverage instead of high precision.
-We modify the rules to (if necessary, add a table of rules here)...
-Technical details here...
 
 %filter features
-\emph{Urban features} distinguish with product aspect in that ...
-Intuitively, a phrase indicating an urban feature must...
-As forth, we use statistics such as ...
+\emph{Urban features} distinguish with product aspect in that it denotes geographical characters of different functional region.
+Intuitively, a phrase indicating an urban feature must be relative to special characters as well as make distinguishment in regions with different labels
+As forth, we use information gain(IG) to selected our urban features as:
 
-Equation here
+\begin{align*}
+IG(word) =& H(C)-H(C|W)\\
+=&-\sum_{i=1}^{k}P(C_i)\log_2P(C_i)+P(word)\sum_{i=1}^{k}P(C_i|word)\log_2P(C_i|word)\\
+&+P(\overline{word})\sum_{i=1}^{k}P(C_i|\overline{word})\log_2P(C_i|\overline{word})
+\end{align*}
+where $P(word)$ is the proportion the word while $P(\overline{word}) = 1- P(word)$;
+$C_i$ denotes the $i$-th class;
+information entropy $H(C)$ reflects the degree of uncertainty of information. The greater the entropy, the more unstable the features are;
+conditional entropy $H(C|W)$ demonstrates the degree of uncertainty after classification according to this feature, and a small conditional entropy denotes a more stable case after classification.
+A high IG value means the word contributes a lot in such a classification.
+and we select features with highest IG value as urban features.
 
-As shown in Table~\ref{tab:urbanfeatures}
+The selected features are shown in Table~\ref{tab:urbanfeatures}
 
@@
 We do not focus on word-level sentiment analysis in this paper.
-The state-of-the-art toolkit is used...
-technical details here
+The common used approach to get sentiment score is based on lexicon.
+We rate the sentiment score of textual data with a existed lexicon with.
+Each word in the lexicon has a trained rate of sentiment.
+With the sopport of stopwords, negative words and adverbs with degree, we could get the sentiment rating of whole sentence.
 
@@
 However, the problem of aggregating word-level sentiments to activity must be addressed.
-intuition here...
-technical details here...
-result is $U_a$, describe
+In the Section~\ref{sec:urbanactivityextraction}, we have group textual data with different activities.
+And in the Section~\ref{sec:urbanfeatureextraction}, we extract urban feature by similarity with activities.
+Due to the similarity we could find enough relevant textual data between each pair of activities and urban features.
+For each activity $a$, we search each urban feature in its corresponding textual data.
+If a sentence in textual data of $a$ contains urban feature $k$, we calculate its sentiment score as a candidate value of $U_{a,k}$.
+The final value of $U_{a,c}$ is the average value of its candidates.
+To fit the sentiment polarity, we map each value of $U_{a,c}$ into the range of $[-1,1]$ by a variant of $sigmoid$ function as:
+$$f(x) =\frac{2}{1+\exp(-x)}-1$$
+Now we get a matrix $U$, which denotes the sentiment on corresponding activities and urban features.
 
@@
 \begin{eqnarray}
-\min \mathcal{L} & =\sum_{f_{r,l,t}\in F}(f_{r,l,t}-\hat{r}_{r,l,t})^2+\lambda_1 (\sum_t b_t^2  + \sum_r \|\mathbf{V}_r\|^2 )\\\nonumber
+\min \mathcal{L} & =\sum_{f_{r,l,t}\in F}(f_{r,l,t}-\hat{f}_{r,l,t})^2+\lambda_1 (\sum_t b_t^2  + \sum_r \|\mathbf{V}_r\|^2 )\\\nonumber
 & +\lambda_2(\sum_l \|\mathbf{c}_l\|_1)+\lambda_3(\sum_i y_i^2)\\\nonumber
@@
 
-\begin{eqnarray}
-inference equation here
+\begin{align*}
+b_t &= b_t - \gamma\left(-2\times\left(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\right)+2\times\lambda_1\times b_t\right)\\
+V_{f,r} &= V_{f,r} - \gamma\left(-2\times\left(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\times\left(\sum_ac_{l,a}\times U_{a,f}\right)\right)+2\times\lambda_1\times V_{f,r}\right)\\
+c_{l,a} &= c_{l,a} - \gamma\left(-2\times(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\times(U_a^TV_r + \beta_{a,t}(\hat{f}_{r,l,t-1})))+\lambda_2\right)\\
+y_i &= y_i - \gamma\left(-2\times\left(\sum_{l,r}(f_{r,l,t} - \hat{f}_{r,l,t})\times\left(\sum_a c_{l,a}\frac{k_h(\hat{f}_{r,l,t-1}-x_j)}{\sum_{j=1}^n k_h(\hat{f}_{r,l,t-1}-x_j)   }\right)\right)+2\times\lambda_3\times y_i\right)\\
 \label{equ:sgd}
-\end{eqnarray}
+\end{align*}
 
@@
 The mobility data (Didi dataset) is a set of  pick-up and drop-off coordinates of taxicabs with timestamps.
-Statistics: e.g. number of pickup-dropoffs , time period, in which city....
-The textual data set (Dianping dataset) is a set of ...
-It is crawled from China's largest online review sits\footnote{www.dianping.com.cn} in ....
-The data set contains xxx POIs, xxx comments
+It contains more than 7 million pick-up and drop-off pairs in November 2016.
+The textual data set (Dianping dataset) is a set of comments of various items. 
+It is crawled from China's largest online review sites\footnote{www.dianping.com.cn} in .... % in what...
+The data set contains 109686 POIs and 3213264 comments.
 
@@
 %preprocessing
-To obtain the input for EFRI, we implement four pre-processing steps: (1) region segmentation; (2) FRI on mobility data; (3) data set linking; (4) text cleaning.
+To obtain the input for EFRI, we implement four pre-processing steps: (1) region segmentation; (2) data set linking; (3)FRI on mobility data; (4) text cleaning.
 
@@
 in other words, how do you get the range?
-We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid by the Raster-based model~\cite{}.
-The road network is converted to a grey image, where in each grid 1 stands for the road and $0$ otherwise. %?????
+We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid by ArcMap, a professional map processing software.
+The road network is converted to a grey image, where in each grid 1 stands for the road and $0$ otherwise.
  The dilation and thinning process~\cite{} is operated to remove small regions such as lanes and road overpasses and simplify the map.
 
-\textbf{FRI on mobility data.} We use DMR~\cite{} to identify region functionals and label them with  8/4 types. % what do you mean by 8/4?
-Any parameters in DMR?
+\textbf{Data set linking.} The common ground of the two datasets is that they both have specific coordinates, which could be corresponding to the rasterized grid exactly.
+For mobility data, we find the traffic flow of each region, and list the flow as vector by time.
+And for POI data, we list the interests of POIs of each region as vector, and the dimension of this vector is equal to the quantity of POIs.
+Now each region has two vectors, and they are the input of DMR.
+
+\textbf{FRI on mobility data.} We use DMR~\cite{Yuan2012FunctionRegion} to identify region functionals and label them with 8 types. 
+DMR is operate with hyper-parameters $\beta = 0.01$, variance $\sigma^2 = 1$
 Note that we can use any convenient FRI system to identify region functionals.
@@
 
-\textbf{Data set linking.} we ??how do you link the two datasets?
-remove any POIs?
-
-\textbf{Text Cleaning.} Chinese word segmentation? stopword removal?
-activity extraction?
+\textbf{Text Cleaning.} 
+A common used package for Chinese word segmentation is Jieba Segment Word.
+We use it to deal with raw textual data and 
+We gather 883 words with less information as stopwords.
+To save memory and improve efficiency, the stopwords are removed from the segmented word list and don't continue the following analysis.
+%activity extraction?  Sec3.1 has done.
 Statistics of the combined dataset are shown in Table~\ref{tab:dataset}.
-Averagely, a POI is associated with xxx comments....more statistics
+Averagely, a POI is associated with nearly 30 comments, a region is related to over 15000 mobility trajectories in 30 days,
+ and a label contains over 100 regions.
 
 \begin{table}[h]
+\centering
 \caption{Statistics of dataset}\label{tab:dataset}
@@
 \#POIs & \#Comments & \#Mobility pairs & \#Regions & \#Labels \\
+\hline
+109686 & 3213264 & 7065937 & 901 & 8 \\
+\hline
 \end{tabular}
@@
 \subsection{Urban Feature Extraction}
+We aim to select suitable urban feature which has a strong distinction on various region functions.
 
-\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) (2) (3) (4) (5)
+\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) Frequency; (2)TF-IDF; (3)rule-based.
 
-\textbf{Evaluation metrics.} (1) (2) (3) (4)equations here
+A simple baseline is to selected the nouns with highest frequency, i.e. appear in as much comments as possible.
+The common approach to extract feature is term frequency¨Cinverse document frequency(TF-IDF) as:
+$$TF-IDF(x) = TF(x)\times IDF(x) = (\log\frac{N}{N(x)})\times(\log\frac{N(x)}{N(x)+1}+1)$$
+where $N$ is the quantity of whole text data ,and $N(x)$ is the quantity of text data contain word $x$
+%Introduction of rule-based.I haven't find related tutorial
+
+\textbf{Evaluation metrics.} These metrics are used to measure our performance:
+(1)Normalization Discounted Cumulative Gain(NDCG); (2)p@n.
+
+To evaluate the accuracy of urban feature extraction, five human volunteers are required to give every selected feature a rating $gain$ of ranges from 1 to 5.
+NDCG is a common used measure, which incorporates graded relevance. The form is:
+\begin{align*}
+DCG_p&=\sum_{i=1}^{p}\frac{gain_i}{\log_2(i+1)}\\
+DCG_p&=\sum_{i=1}^{|REL|}\frac{gain_i}{\log_2(i+1)}\\
+NDCG_p&= \frac{DCG}{IDCG}
+\end{align*}
+NDCG@$k$ means that $k$ features are selected to be evaluated.
+And p@n represents the proportion of features with cumulative Gain higher than 2 in n selected urban features.
 
 \begin{table}[h]
+\centering
 \caption{Comparative performance of urban feature extraction}\label{tab:extraction}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{p{3.3cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}}
         \hline
-Method & Metric 1 & Metric 2 & Metric 3 & Metric 4\\\hline
+        Extraction approach & p@5 & p@10 & p@15 & NDCG@3 & NDCG@5\\
+        \hline
+        Frequency &  &  &  & \\
+        \hline
+        TF-IDF &  &  &  & \\
+        \hline
+        rule-based &  &  &  & \\
+        \hline
+        EFRI &  &  &  & \\
+        \hline
     \end{tabular}
@@
 
-As shown in Table~\ref{tab:extraction}, your analysis here.
+As shown in Table~\ref{tab:extraction}, We can see that our EFRI model has a superior performance of urban feature extraction.
+
+\subsection{Traffic Flow Prediction}
+
+\textbf{Comparative Methods.} The prediction of EFRI is operated with layered regression.
+There is some other approaches can estimate the prediction. (1)collaborative filtering; (2)EFRI withour bias curve $\beta$; (3) EFRI with normal feature.
+
+CF is widely used in recommendation system.Therefore, prediction is one of the most application of CF.
+Meanwhile, we compare with the variant form of EFRI to validate its advantage.
+
+\textbf{Evaluation metrics.}It is a typical regression process and common used evaluate matrix is: (1)Mean Squared Error(MSE), (2)Root Mean Squared Error(RMSE), (3)Mean Absolute Error(MAE) (4)R Squared($R^2$).
+
+They are typical metrics to measure the accuracy of regression model, and their form as:
+$$MSE = \frac{1}{m}(y_i-\hat{y}_i)^2$$
+$$RMSE = \sqrt{\frac{1}{m}(y_i-\hat{y}_i)^2}$$
+$$MAE = \frac{1}{m}|y_i-\hat{y}_i|$$
+$$R^2 = 1-\frac{MSE(\hat{y} , y)}{Var(y)}$$
+where $y$ is the real value and $\hat{y}$ is the predict value given by regression;
+$Var(y)$ is the variance of $y$.
+
+\begin{table}[h]
+    \centering
+    \caption{Comparative performance of traffic flow prediction}\label{tab:prediction}
+    \begin{tabular}{p{3.3cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}|p{1.6cm}}%{c|c|c|c|c|c}
+        \hline
+        Prediction Approach & MSE & RMSE & MAE & $R^2$ \\
+        \hline
+        CF &  &  &  & \\
+        \hline
+        EFRI without $\beta$ &  &  &  & \\
+        \hline
+        EFRI with normal feature &  &  &  & \\
+        \hline
+        EFRI &  &  &  & \\
+        \hline
+    \end{tabular}
+\end{table}
+From Table~\ref{tab:prediction}, we confirm our confidence that EFRI has a more accurate result than other approaches in most metrics.
+It turn out that EFRI could capture the interesting information in mobility patterns.
+EFRI perform better than the same framework with normal feature, which also proves the accuracy of our urban feature extraction.
+
+Besides, the variable $y_i$ corresponding to $x_i$ have been learn by EFRI, and we get parameter of $\beta(x)$.
+The form of $\beta(x)$ with trained $y_i$ is shown in Figure~\ref{fig:beta}
+\begin{figure}[h]
+  \centering
+  \label{fig:beta}
+  \caption{The form of $\beta$ with a=1, t=weekend}
+\end{figure}
 
@@
 
-\textbf{Comparative Methods.} We compare EFRI with the following systems. (1) (2) (3)
+\textbf{Comparative Methods.} We compare EFRI with the following systems. (1)text-based explanation; (2)trajectory-based explanation.
+
+EFRI based on the mixture application of mobility data and textual data.
+We set the explanation given by a single data source as baseline to discuss the result of the heterogeneous data.
 
@@
 The first is objective to evaluate the quantity of explanations.
-(1) EP: percentage of regions that could find explanation label by our framework.
-The rest are subjective to evaluate the quality of explanations.
-(2) (3) (4) All reported results are averaged over regions.
+(1)explainability precision(EP); (2)Explain quality.
 
-equations here 
+To measure the explainability of these models, ~\cite{Abdollahi2017MEPMER} adopted MAP and MAR as evaluation metrics.
+EP is percentage of regions that could find explanation label by our framework, which is defined as:
 $$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$
+And the rest are subjective to evaluate the quality of explanations.
 
-\textbf{Evaluation Process}  how many human judges? how to vote?
+All reported results are averaged over regions.
+
+\textbf{Evaluation Process}
+To measure the quality of explainability, five human volunteers are required to give every urban feature as explanation a rating.
+The accurate labels get 5 stars while the incorrect get 1 star.
+Our evaluation based on the average of the rating over humans.
 
 \begin{table}[h]
+\centering
 \caption{Comparative performance of explainability }\label{tab:explainablity}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{p{3.3cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}}
         \hline
-Method & Metric 1 & Metric 2 & Metric 3 & Metric 4\\\hline
+        Method & EP & Explain quality\\
+        \hline
+        text-based &  & \\
+        \hline
+        Trajectory-besed &  & \\
+        \hline
+        EFRI &  & \\
+        \hline
     \end{tabular}
@@
 
-As shown in Table~\ref{tab:explainability}, your analysis here.
+As shown in Table~\ref{tab:explainablity}, EFRI is outperformed than the baselines with single data source in both EP and quality.
+It demonstrates that our mixture of the heterogeneous data improve the interpretability of FRI results.
 
@@
 \bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
-    Zhang Y, Lai G, Zhang M, et al.
+\bibitem{Zhang2014ExplicitFactor}Zhang Y, Lai G, Zhang M, et al.
 Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval.
@@
 \bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
+\bibitem{Mikolov2013Word2vec}Mikolov T , Sutskever I , Chen K , et al.
+Distributed Representations of Words and Phrases and their Compositionality[J].
+Advances in Neural Information Processing Systems, 2013, 26:3111-3119.
+\bibitem{Abdollahi2017MEPMER}Behnoush Abdollahi and Olfa Nasraoui.
+Using explainability for constrained matrix factorization.
+In Proceedings of the Eleventh ACM Conference on Recommender Systems, pages 79¨C83.
+ACM, 2017.
 \end{thebibliography}

### 2018-11-26 paper.tex
overview图和整理参考文献

@@
 Recently, urban computing has attracted attentions from both academy and industry.
-One critical step towards efficient urban computing is to identify \emph{functional regions}, which are regions in a city that support certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+One critical step towards efficient urban computing is to identify \emph{functional regions}, which are regions in a city that support certain needs of urban lives~\cite{Yuan2018FunctionRegion}.
 
@@
 Most of previous \emph{Functional Region Identification} (FRI) systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}.
-For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, variants of Latent Dirichlet Allocation (LDA) is applied on remote-sensor data~\cite{Vatsavai2010Remote} and taxicab pick-ups and drop-offs data~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, variants of Latent Dirichlet Allocation (LDA) is applied on remote-sensor data~\cite{Vatsavai2010Remote} and taxicab pick-ups and drop-offs data~\cite{Yuan2018FunctionRegion}.
 
@@
 the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means.
-Furthermore, to obtain accurate identification, recent research tends to use complex models such as the Dirichlet Multinomial Regression model in~\cite{Yuan2015FunctionRegion} .
+Furthermore, to obtain accurate identification, recent research tends to use complex models such as the Dirichlet Multinomial Regression model in~\cite{Yuan2018FunctionRegion} .
 The complex nature of these models is an obstacle for people to capture the ``semantics'' of the clustering results.
@@
 \centering
-\includegraphics[scale=0.5]{overview.png}
+\includegraphics[scale=0.45]{overview.png}
 \caption{An illustrative example of Explainable Functional Region Identification (EFRI)}
@@
 Major sources of mobility data are check-ins data~\cite{Cheng2011Check-in,Gallegos16happier}, origin-destination pairs data~\cite{Ge2011TaxiBusiness,Meng2017Traffic}  and trajectory data~\cite{Ge2011TaxiBusiness,Garg2018Route,Wu2017Reachable,Wang2018Deep}.The simplest form among them are check-ins data, which is a set of points revealing users' current locations collected from location sharing services.
-Check-ins data are previously adopted for revealing demographic associations~\cite{Gallegos16happier} and POI recommendation~\cite{Cheng2011Check-in}.
+Check-ins data are previously adopted for revealing demographic associations~\cite{Gallegos16happier} and POI recommendation~\cite{Cheng2011Check-in,Zhao2016POI}.
 Origin-destination data consists of a set of pairwise location points, e.g.
-a pick-up point and a drop-off point of a taxi trajectory.
-Most functional region identification systems are based on origin-destination pairs~\cite{,Karlsson2006FunctionalRegionSummary}, e.g.
+a pick-up point and a drop-off point of a taxi trajectory~\cite{Yuan2010NextPassenger,Zheng2011taxicabs}.
+Most functional region identification systems are based on origin-destination pairs~\cite{Karlsson2006FunctionalRegionSummary}, e.g.
 from commute data~\cite{Farmer2009Overvie, Korpan2017navigation,Jose2018cognitive}, or from remote-sensor image data~\cite{Vatsavai2011Remote}.
@@
 Recent studies focus on city-level FRI, i.e.
-identification of regions in a city that support certain needs of urban lives ~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+identification of regions in a city that support certain needs of urban lives ~\cite{Yuan2018FunctionRegion}.
 Traditional FRI systems are rule-based~\cite{Ball1980Definition}, i.e.
@@
 Most of them use clustering methods~\cite{Karlsson2006FunctionalRegionSummary}.
-To name a few, clustering algorithm based on the 'modularity function'~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering~\cite{Vatsavai2011Remote}, Latent Dirichlet Allocation (LDA)~\cite{Vatsavai2010Remote} and Dirichlet Multinomial Regression (DMR)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
+To name a few, clustering algorithm based on the 'modularity function'~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering~\cite{Vatsavai2011Remote}, Latent Dirichlet Allocation (LDA)~\cite{Vatsavai2010Remote} and Dirichlet Multinomial Regression (DMR)~\cite{Yuan2018FunctionRegion}.
 
@@
 \subsection{Online Review Analysis}
-Online review data has been extensively studied in opinion mining~\cite{}.
-Given a set of product features, the user sentiments in each review are extracted either as binary sentiment polarity~\cite{} or as numerical sentimental strength~\cite{}.
-Opinion mining has been combined with recommender systems to generate explainable recommendations~\cite{}.
-Typically, a latent factor model~\cite{} is utilized to decompose user-item ratings to a latent feature space of user preferences and item attributes.
+Online review data has been extensively studied in opinion mining~\cite{Zhang2018Survey}.
+Given a set of product features, the user sentiments in each review are extracted either as binary sentiment polarity~\cite{Zhang2015Sentires} or as numerical sentimental strength~\cite{Stieglitz2013SentimentStrenth}.
+Opinion mining has been combined with recommender systems to generate explainable recommendations~\cite{Zhang2014ExplicitFactor}.
+Typically, a latent factor model~\cite{Zhang2014ExplicitFactor} is utilized to decompose user-item ratings to a latent feature space of user preferences and item attributes.
 Though there are fruitful research results in this domain, due to the lack of geographical analysis, these methods are not directly applicable to generate explanations for FRI.
@@
 \end{align*}
+where $\gamma$ is the learning rate.
 
@@
 The textual data set (Dianping dataset) is a set of comments of various items.
-It is crawled from China's largest online review sites\footnote{www.dianping.com.cn} in .... % in what...
+It is crawled from China's largest online review sites\footnote{www.dianping.com.cn} Before August 2018.
+We search for all corresponding items with 16 tags located within five center districts in the city respectively.
+Most introduction page of each item also provides the coordinate and comments of it.
 The data set contains 109686 POIs and 3213264 comments.
@@
 \textbf{Region segmentation.} To form the basic city regions, we segment the urban area by the city's major road network.
-The longitude of the map range in Didi dataset is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.% do we have to provide the range?
-in other words, how do you get the range?
+The longitude of the map range in Didi dataset is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.
+Most of the POIs also located within the area.
 We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid by ArcMap, a professional map processing software.
 The road network is converted to a grey image, where in each grid 1 stands for the road and $0$ otherwise.
- The dilation and thinning process~\cite{} is operated to remove small regions such as lanes and road overpasses and simplify the map.
+The dilation and thinning process~\cite{Yuan2018FunctionRegion} is operated to remove small regions such as lanes and road overpasses and simplify the map.
 
@@
 
-\textbf{FRI on mobility data.} We use DMR~\cite{Yuan2012FunctionRegion} to identify region functionals and label them with 8 types. 
+\textbf{FRI on mobility data.} We use DMR~\cite{Yuan2018FunctionRegion} to identify region functionals and label them with 8 types.
 DMR is operate with hyper-parameters $\beta = 0.01$, variance $\sigma^2 = 1$
@@
 Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.
-
-\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
-
-\bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y.
-City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories.
-Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10
-
+\bibitem{Yuan2018FunctionRegion}Yuan N J, Zheng Y, Xie X. Discovering Functional Zones in a City Using Human Movements and Points of Interest[J]. 2018.
+\bibitem{Karlsson2006FunctionalRegionSummary}Karlsson C, Olsson M. The identification of functional regions: theory, methods, and applications[J]. Annals of Regional Science, 2006, 40(1):1-18.
+\bibitem{Newman2004ModularityFunction}Newman M E J. Detecting community structure in networks[J]. European Physical Journal B, 2004, 38(2):321-330.
+\bibitem{Ratti2010Telecom}Ratti C, Sobolevsky S, Calabrese F, et al. Redrawing the Map of Great Britain from a Network of Human Interactions[J]. Plos One, 2010, 5(12):e14248.
 \bibitem{Vatsavai2011Remote}Vatsavai R R, Bright E, Varun C, et al.
@@
 DBLP, 2011:1-10.
-
 \bibitem{Vatsavai2010Remote}Vatsavai R R, Cheriyadat A, Gleason S.
@@
 IEEE Computer Society, 2010:273-280.
-
-\bibitem{Ratti2010Telecom}Ratti C, Sobolevsky S, Calabrese F, et al. Redrawing the Map of Great Britain from a Network of Human Interactions[J]. Plos One, 2010, 5(12):e14248.
-
-\bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
-\bibitem{Ge2011TaxiBusiness}Ge Y, Liu C, Xiong H, et al.
-A taxi business intelligence system[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, San Diego, Ca, Usa, August.
-DBLP, 2011:735-738.
-\bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp
-
-\bibitem{Garg2018Route}Nandani Garg and Sayan Ranu.
-Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!.
-In KDD 18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19-23, 2018, London, United Kingdom.
-2018.
-
-\bibitem{Goddard1970EarliestFunction}Goddard J B.
-Functional Regions within the City Centre: A Study by Factor Analysis of Taxi Flows in Central London[J].
-Transactions of the Institute of British Geographers, 1970, 49(49):161-182.
-
-\bibitem{Karlsson2006FunctionalRegionSummary}Karlsson C, Olsson M. The identification of functional regions: theory, methods, and applications[J]. Annals of Regional Science, 2006, 40(1):1-18.
-
-\bibitem{Newman2004ModularityFunction}Newman M E J. Detecting community structure in networks[J]. European Physical Journal B, 2004, 38(2):321-330.
-
-\bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
-\bibitem{Yuan2012FunctionRegion}Yuan J, Zheng Y, Xie X.
-Discovering regions of different functions in a city using human mobility and POIs[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining.
-ACM, 2012:186-194.
-
-\bibitem{Yuan2015FunctionRegion}Yuan N J, Zheng Y, Xie X, et al.
-Discovering Urban Functional Zones Using Latent Activity Trajectories[J].
-Knowledge \& Data Engineering IEEE Transactions on, 2015, 27(3):712-725.
-
-\bibitem{Yuan2018FunctionRegion}Yuan N J, Zheng Y, Xie X. Discovering Functional Zones in a City Using Human Movements and Points of Interest[J]. 2018.
-
-\bibitem{Zhang2015Fuel}Zhang F, Yuan N J, Wilkie D, et al.
-Sensing the Pulse of Urban Refueling Behavior:A Perspective from Taxi Mobility[J].
-Acm Transactions on Intelligent Systems \& Technology, 2015, 6(3):1-23.
-
-\bibitem{Shang2014Pollution}Shang J, Zheng Y, Tong W, et al. Inferring gas consumption and pollution emission of vehicles throughout a city[J]. 2014:1027-1036.
-
-\bibitem{Wu2017Reachable}Wu G, Ding Y, Li Y, et al. Mining Spatio-Temporal Reachable Regions over Massive Trajectory Data[C]// IEEE, International Conference on Data Engineering. IEEE, 2017:1283-1294.
-
-\bibitem{Wang2018Deep}D Wang,J Zhang,W Cao,J Li,Y Zheng.When Will You Arrive? Estimating Travel Time Based on Deep Neural Networks.In International AAAI Conference on Web and Social Media, 2011.
-
-\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1-13, 2015
-
-\bibitem{Alshamsi15milan}Alshamsi A, Awad E, Almehrezi M, et al. Misery loves company: happiness and communication in the city[J]. Epj Data Science, 2015, 4(1):7.
-
-\bibitem{Cheng2011Check-in}Z. Cheng, J. Caverlee, K. Lee, and D. Sui. Exploring millions of footprints in location sharing services. In International AAAI Conference on Web and Social Media, 2011.
-
-\bibitem{Gonzlez2008Track}Gonzlez M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
-
-\bibitem{Gallegos16happier}Gallegos L, Huang A, Huang A, et al.
-Geography of Emotion: Where in a City are People Happier?[C]// International Conference Companion on World Wide Web.
-International World Wide Web Conferences Steering Committee, 2016:569-574.
-
-\bibitem{Zhao2016POI}Zhao S, King I, Lyu M R. A Survey of Point-of-interest Recommendation in Location-based Social Networks[J]. 2016.
-
-\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. arXiv preprint arXiv:1804.11192. 2018.
-
-\bibitem{Herlocker2000Explanation} Herlocker J L, Konstan J A, Riedl J. Explaining collaborative filtering recommendations[C]// Acm Conference on Computer Supported Cooperative Work. 2000:241-250.
-
-\bibitem{Ferwerda2012ContentCorrelate} Ferwerda B, Swelsen K, Yang E. Explaining Content-Based Recommendations[J]. Bruceferwerda Com.
-
-\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
-\bibitem{Zhang2014ExplicitFactor}Zhang Y, Lai G, Zhang M, et al.
-Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval.
-ACM, 2014:83-92.
-
-\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017
 \bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63-72.
-    %explain AI
 \bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator.
@@
 DBLP, 2011:347-356.
-\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S .
-Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems.
-ACM, 2017.
-\bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
+\bibitem{Cheng2011Check-in}Z. Cheng, J. Caverlee, K. Lee, and D. Sui. Exploring millions of footprints in location sharing services. In International AAAI Conference on Web and Social Media, 2011.
+\bibitem{Gallegos16happier}Gallegos L, Huang A, Huang A, et al.
+Geography of Emotion: Where in a City are People Happier?[C]// International Conference Companion on World Wide Web.
+International World Wide Web Conferences Steering Committee, 2016:569-574.
+\bibitem{Ge2011TaxiBusiness}Ge Y, Liu C, Xiong H, et al.
+A taxi business intelligence system[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, San Diego, Ca, Usa, August.
+DBLP, 2011:735-738.
+\bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y.
+City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories.
+Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10
+\bibitem{Garg2018Route}Nandani Garg and Sayan Ranu.
+Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!.
+In KDD 18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19-23, 2018, London, United Kingdom.
+2018.
+\bibitem{Wu2017Reachable}Wu G, Ding Y, Li Y, et al. Mining Spatio-Temporal Reachable Regions over Massive Trajectory Data[C]// IEEE, International Conference on Data Engineering. IEEE, 2017:1283-1294.
+\bibitem{Wang2018Deep}D Wang,J Zhang,W Cao,J Li,Y Zheng.When Will You Arrive? Estimating Travel Time Based on Deep Neural Networks.In International AAAI Conference on Web and Social Media, 2018.
+\bibitem{Zhao2016POI}Zhao S, King I, Lyu M R. A Survey of Point-of-interest Recommendation in Location-based Social Networks[J]. 2016.
+\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
+\bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
+\bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp
+\bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
+\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. arXiv preprint arXiv:1804.11192. 2018.
+\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
+\bibitem{Stieglitz2013SentimentStrenth}Stieglitz S , Dang-Xuan L .
+Emotions and Information Diffusion in Social Media¡ªSentiment of Microblogs and Sharing Behavior[J].
+Journal of Management Information Systems, 2013, 29(4):217-248.
+\bibitem{Zhang2014ExplicitFactor}Zhang Y, Lai G, Zhang M, et al.
+Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval.
+ACM, 2014:83-92.
+\bibitem{Gonzlez2008Track}Gonzlez M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
+\bibitem{Alshamsi15milan}Alshamsi A, Awad E, Almehrezi M, et al. Misery loves company: happiness and communication in the city[J]. Epj Data Science, 2015, 4(1):7.
+\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1-13, 2015
 \bibitem{Mikolov2013Word2vec}Mikolov T , Sutskever I , Chen K , et al.
@@
 ACM, 2017.
+
+\bibitem{Herlocker2000Explanation} Herlocker J L, Konstan J A, Riedl J. Explaining collaborative filtering recommendations[C]// Acm Conference on Computer Supported Cooperative Work. 2000:241-250.
+\bibitem{Ferwerda2012ContentCorrelate} Ferwerda B, Swelsen K, Yang E. Explaining Content-Based Recommendations[J]. Bruceferwerda Com.
+\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S .
+Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems.
+ACM, 2017.
 \end{thebibliography}
